# ---
# title = "ucoa master doc"
# output = html-document
# ---

# 0. Program Description

**Purpose**
I am interested in learning more about how to access and pay with the UCOA codes. I decided to conduct some Exploratory Data Analysis in this document as well. This script is not really meant for a single button run-all. It rather is built to allow a data analyst to play around with the data easily. It does contain a few basic reports and interesting plots. 

Some noteworthy naming conventions:
OSA = Office of the State Auditor. It is meant to distinguish usages of the OSA's UCA code in comparison to USOE/LEA, STATE, and higher-education UCAs.

LEA = Utah State Board of Education UCA. It applies for LEA. 

DURATION: the script will take about 20-30 minutes to run.

**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "salesforce"
```

**Output(s)**


# I. Libraries and Data Sources

```{r}
options(scipen=999)

library(lubridate)
library(magrittr)
library(odbc)
library(readxl) 
library(tidyverse)
library(stringi) 

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)

rm(dsn_aws, dsn_salesforce)

```


# II. Function Definitions

## 1. agg_dollars_and_records
```{r}
agg_dollars_and_records<- function(df, ...){
  # Purpose: groups the data by supplied grouping variables, and aggregates the
  # date to have a total dollar amount and a count for the number of transactions
  # with such variables. Basically this will group uca codings into dollar and
  # frequency amounts. Two metrics of interest to Alex.
  #
  # Inputs: *df (tibble or dataframe): a dataframe which has the grouping variables. it should have an amount column
  #         *... : the grouping variables. should be a uca field.
  # Outputs: tibble :an aggregated tibble
  
  grouping_vars <- enquos(...)
  
  agg_table <- df %>% 
    group_by(!!! grouping_vars) %>% 
    summarize(total_amount = sum(amount),
              num_of_trans = n()) %>% 
    arrange(desc(total_amount))
  
}
```


```{r}
barplot_amount <- function(templist,agg_by_type, agg_type, uca_block, temprange){
  # Description
  # 
  # Inputs: templist (list):
  #         agg_by_type(string/char):  used to decide whether to pluck by_description_and_code, by_description, or by_code
  #         agg_type(string/char): used to pluck a specific type of aggregat table such as agg_fund or agg_function
  #         uca_block(object?): the uca block of interest, ex: fund, location, object...
  #         temprange(int): a range of interest. for example : 4000 ==> 40000000
  # 
  # Outputs:
  #         p (ggplot object)
  
  uca_block <-enquo(uca_block)
  
  p <- templist %>%
    pluck(agg_by_type) %>%
    pluck(agg_type) %>%
    filter(str_detect(!!uca_block, paste0("^", temprange))) %>%
    ggplot(aes(x = !!uca_block, y = total_amount)) +
    geom_bar(stat = "identity", fill = "lightcoral") +
    coord_flip() +
    geom_text(
      aes(label = paste0("$", total_amount)),
      hjust = "inward",#-.25,
      vjust = "inwward",#0,
      size = 3
    ) +
    labs(title = paste0(
      "barplot of ",
      rlang::as_name(uca_block),
      " starting with: ",
      temprange
    ))
  p

}

```


```{r}
barplot_description_amount <- function(templist,agg_by_type, agg_type,uca_block, uca_block_description, temprange){
  # Description
  # 
  # Inputs: templist (list):
  #         agg_by_type(string/char):  used to decide whether to pluck by_description_and_code, by_description, or by_code
  #         agg_type(string/char): used to pluck a specific type of aggregat table such as agg_fund or agg_function
  #         uca_block(object?): the uca block of interest, ex: fund, location, object...
  #         temprange(int): a range of interest. for example : 4000 ==> 40000000
  # 
  # Outputs:
  #         p (ggplot object)
  uca_block <-enquo(uca_block)
  uca_block_description <-enquo(uca_block_description)
  
  p <- templist %>%
    pluck(agg_by_type) %>%
    pluck(agg_type) %>%
    filter(str_detect(!!uca_block, paste0("^", temprange))) %>%
    ggplot(aes(x = !!uca_block_description, y = total_amount)) +
    geom_bar(stat = "identity", fill = "steelblue2") +
    coord_flip() +
    geom_text(
      aes(label = paste0("$", total_amount)),
      hjust = "inward",#-.25,
      vjust = "inwward",#0,
      size = 3
    ) +
    labs(title = paste0(
      "barplot of ",
      rlang::as_name(uca_block_description),
      " starting with: ",
      temprange
    ))
  p

}


```

# III. LOAD, QUERY, and WRANGLE

## 1. OSA

```{r}
osa_file_name <- "ucoa.xlsx"

# fund =========================================================================
osa_fund <-
  read_xlsx(osa_file_name, sheet = excel_sheets(osa_file_name)[[1]]) %>%
  mutate(number = number %>% str_pad(3, pad = "0"))


# add additional fund numbers.
extra_fund_numbers <-
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    short_description = NA,
    full_description = case_when(
      number %in% (202:298) ~ "Special Revenue Funds (as assigned by local government)",
      number %in% (302:398) ~ "Debt Service Funds (as assigned by local government)",
      number %in% (402:448) ~ "Capital Projects Funds (as assigned by local government)",
      number %in% (452:498) ~ "Permanent Funds (as assigned by local government)",
      number %in% (502:598) ~ "Enterprise Funds (as assigned by local government)",
      number %in% (602:698) ~ "Internal Service Funds (as assigned by local government)",
      number %in% (702:798) ~ "Trust and Agency Funds (as assigned by local government)"
    ),
    "detail" = NA
  )

osa_fund <-
  osa_fund %>%
  bind_rows(extra_fund_numbers) %>%
  select(number, description = full_description)

# funct ========================================================================
osa_funct <-
  read_xlsx(osa_file_name, sheet = excel_sheets(osa_file_name)[[2]]) %>%
  mutate(number = as.character(number)) %>%
  select(number, description = full_description)

osa_funct$number[[1]] <- "000000"

# account ======================================================================
osa_account <-
  read_xlsx(osa_file_name, sheet = excel_sheets(osa_file_name)[[3]]) %>%
  mutate(number = as.character(number)) %>%
  select(number, description = full_description)

# consolidate ==================================================================
osa_lookup <-
  list(fund        = osa_fund,
       funct       = osa_funct,
       account     = osa_account)

```
Remove unneeded objects
```{r}
rm(osa_fund, osa_funct, osa_account, extra_fund_numbers , osa_file_name)
```


## 2. USBE
```{r}
# fund =========================================================================
usbe_file_name <- "FY20 COA-USBE.xlsx"

usbe_fund <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[1]]) %>% 
  rename(number = FundCode,
         description = FundDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

##add back the ranges
extra_fund_numbers <- c(27:29, 61:69) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    description =
      case_when(
        number %in% (27:29) ~ "Special Revenue Funds - (Assigned by District)",
        number %in% (61:69) ~ "Interal Service Fund - (Assigned by District)"
      ),
    can_submit = TRUE
  )

usbe_fund <-
  usbe_fund %>%
  bind_rows(extra_fund_numbers)

# Location =====================================================================   
usbe_location<- c(0:499,600:999) %>%
  # str_pad(3, pad = "0") %>% 
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
    mutate( description =
      case_when(
        as.numeric(number) <= 10    ~ "Pre School",
        as.numeric(number) >= 11 & as.numeric(number) <= 99   ~ "District Level",
        number %in% (100:299) ~ "Elementary Schools",
        number %in% (300:399) ~ "Middle Schools",
        number %in% (400:499) ~ "Junior High Schools/Middle Schools",
        number %in% (600:699) ~ "Special Schools, Secondary",
        number %in% (700:799) ~ "High Schools",
        number %in% (800:899) ~ "Special Schools, Elementary",
        number %in% (900:975) ~ "Private Schools",
        number %in% (976:999) ~ "Adult Education Schools"
      ),
      can_submit = TRUE
      ) %>% 
  mutate(number = number %>% str_pad(3, pad = "0")) 
  

# program  =====================================================================
usbe_program <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[2]]) %>%
  rename(number = ProgramCode,
         description = ProgramDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = number %>% str_pad(4, pad = "0"))

extra_program_numbers <- c(
  2000:3699,
  # 2000 SCHOOL LEVEL PROGRAMS
  5251:5290,
  7804:7809,
  7811:7819,
  7821:7829,
  7831:7839,
  7841:7849,
  7851:7859,
  7871:7879,
  7891:7899,
  7916:7919,
  7911:7914,
  7921:7929,
  7931:7939,
  7941:7949,
  7951:7959
) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    description =
      case_when(
        number %in% (2000:2099) ~ "General School",
        number %in% (2100:2199) ~ "General Studentbody",
        number %in% (2200:3299) ~ "Instructional Classes",
        number %in% (3300:3599) ~ "Other Instructional Classes",
        number %in% (3600:3699) ~ "Student Activity Funds",
        
        number %in% (5251:5259) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        number %in% (5260:5269) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        number %in% (5270:5290) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        
        number %in% (7804:7809) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7811:7819) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7821:7829) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7831:7839) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7841:7849) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7851:7859) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7871:7879) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7891:7899) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7916:7919) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7911:7914) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7921:7929) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7931:7939) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7941:7949) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7951:7959) ~ "(NCLB) Numbers reserved for districts"
      ),
    can_submit = TRUE
  )

usbe_program <-
  usbe_program %>%
  bind_rows(extra_program_numbers)  

# Function =====================================================================
usbe_funct <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[4]]) %>%
  rename(number = FunctionCode,
         description = FunctionDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

# Object =======================================================================

usbe_object <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[5]]) %>%
  rename(number = ObjectCode,
         description = ObjectDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

# Revenue Classification" ======================================================
usbe_revenue <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[3]]) %>%
  rename(number = RevenueCode,
         description = RevenueDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

# Many LEA put 0000 for their revenue code. To keep them from all being removed,
# I created a temporary holder. I will likely change the name once I understand
# why this code is always being used.
extra_revenue_numbers <- c("0000") %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    description =
      case_when(number == "0000" ~ "TEMPORARY HOLDER - ALEX NIELSON",),
    can_submit = TRUE
  )

usbe_revenue <-
  usbe_revenue %>%
  bind_rows(extra_revenue_numbers)


#consolidate ===================================================================
usbe_lookup <- list(
  fund     = usbe_fund,
  location = usbe_location,
  program  = usbe_program,
  funct    = usbe_funct,
  object   = usbe_object,
  revenue  = usbe_revenue
)

```
Remove unneeded objects
```{r}
rm(
  usbe_fund,
  usbe_location,
  usbe_funct,
  usbe_program,
  usbe_revenue,
  usbe_object,
  extra_program_numbers,
  extra_fund_numbers,
  extra_revenue_numbers,
  usbe_file_name
)
```



#IV. Load and Validate UCOA codes
 *We will vadidate the code to remove missing values, and "". Then generate for three main reports. The first report contains both invalid LEA and NON-LEA codes. THe second report will be valid LEA codes (lea_reported_ucoa). The third report will be valid NON-LEA codes (I call it osa_reported_ucoa)

## 1. Query AWS transaction table
```{r}

# Query the database, get all the records that are not obviously missing data. 
reported_ucoa <-
dbGetQuery(
  odbc_aws,
  paste("
        SELECT id, 
        batch_id,
        amount,
        fiscal_year,
        account_number,
        type
        FROM transaction
        WHERE account_number IS NOT NULL
        LIMIT 1000000")) %>% # note I am limitingto 10000000 so it doesn't take an eternity.
as_tibble() 

# double check for NA or "" ----------------------------------------------------

invalid_reported_na_or_empty <- reported_ucoa %>%
  filter(account_number=="",
        is.na(account_number))

reported_ucoa <- 
  reported_ucoa %>% 
  filter(account_number != "", !is.na(account_number))

#check correct length ----------------------------------------------------------

# 19 is for normal, 25 is for LEA. (dashes are included in string legth)
invalid_ucoa_length <- reported_ucoa %>% 
  filter(nchar(account_number) != 19 && nchar(account_number)!= 25) %>% 
  mutate(account_number_length = nchar(account_number),
         reason = case_when(account_number_length < 19 ~ "uca code too short for non LEA",
                            account_number_length > 19 & account_number_length<25 ~ "uca code incorrect length",
                            account_number_length > 25 ~ "uca code too long for LEA"))

reported_ucoa <- reported_ucoa %>% 
  filter(nchar(account_number) == 19 || nchar(account_number)== 25)


# Generate temp tibbles --------------------------------------------------------
# this will help with the subsequent reports. You could condense this, but for
# my mind this is easier to debugg and catch flaws. 

#filter for only lea
usbe_reported_ucoa <- reported_ucoa %>% filter(nchar(account_number)== 25)

#filter for non USBE
osa_reported_ucoa <- reported_ucoa %>% filter(nchar(account_number)== 19)

# USBE ==========================================================================

# check if the codes are valid form. ie: ##-###-####-####-###-#### 
 
invalid_usbe_ucoa_code <-
  usbe_reported_ucoa %>%
  filter(!str_detect(
    usbe_reported_ucoa$account_number,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))

usbe_reported_ucoa <-
  usbe_reported_ucoa %>%
  filter(str_detect(
    usbe_reported_ucoa$account_number,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))

# non lea ====================================================================== 

# check if the codes are valid form. ie: ###-######-########  

invalid_osa_ucoa_codes <- osa_reported_ucoa %>%
  filter(!str_detect(
    osa_reported_ucoa$account_number,
    regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")
  ))

osa_reported_ucoa <-
  osa_reported_ucoa %>%
  filter(str_detect(
    osa_reported_ucoa$account_number,
    regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")
  ))

# consolidate ==================================================================
osa_ucoa <- osa_reported_ucoa
usbe_ucoa <- usbe_reported_ucoa
invalid_tables <-
  list(invalid_reported_na_or_empty,
       invalid_ucoa_length,
       invalid_usbe_ucoa_code,
       invalid_osa_ucoa_codes)
names(invalid_tables) <- c("na_or_empty",
                           "invalid_length",
                           "invalid_lea_format",
                           "invalid_osa_format")

# remove unneeded objects ======================================================
# comment any object that you want to inspect in the global environment pane
rm(
  invalid_reported_na_or_empty,
  invalid_usbe_ucoa_code,
  invalid_osa_ucoa_codes,
  invalid_ucoa_length,
  osa_reported_ucoa,
  usbe_reported_ucoa,
  reported_ucoa
)
  
```

##2. OSA 

### a. Enrich OSA ucoa tibble 
```{r}
# This breaks out the account numbers into fund, function, and account. 
osa_ucoa <- osa_ucoa%>% 
  mutate(
    fund = .[["account_number"]] %>% substr(0, 3),
    funct = .[["account_number"]] %>% substr(5, 10),
    account = .[["account_number"]] %>%  substr(12, 19),
  ) %>% 

# Now we need to join ucoa.xlsx, so we know what the codes mean.

# join the funds
  left_join(
    osa_lookup %>% 
      pluck("fund") %>%
      as_tibble() %>%
      select(number, fund_description = description),
    by = c("fund" = "number")
  ) %>%
  # join the functions
  left_join(
    osa_lookup %>% 
      pluck("funct") %>%
      as_tibble() %>%
      select(number, funct_description = description),
    by = c("funct" = "number")
  ) %>%
  # join the accounts
  left_join(
    osa_lookup %>%
      pluck("account") %>%
      as_tibble() %>%
      select(number, account_description = description),
    by = c("account" = "number")
          )
```
### b. Find unmapped OSA UCA 
*There are many reasons why this might be the case 
**They are using an old UCOA
**They pressed the incorrect key / typos
...regardless, they must be filtered out. 

```{r}
#find wrong fund code
osa_bad_fund_code <- osa_ucoa %>%
  filter(!fund %in% (osa_lookup %>%
                       pluck("fund")  %>%
                       select(number) %>%
                       unlist()))
#find wrong function code
osa_bad_funct_code<-osa_ucoa %>%
  filter(!funct %in% (osa_lookup %>%
                        pluck("funct") %>%
                        select(number) %>%
                        unlist()))
#find wrong account code
osa_bad_account_code <- osa_ucoa %>%
  filter(!account %in% (osa_lookup %>%
                          pluck("account") %>%
                          select(number)   %>%
                          unlist()))


#now remove incorrectly mapped. we will save them to report, but do not want
#them in our analysis.
osa_ucoa<- osa_ucoa %>% 
  anti_join(osa_bad_fund_code, by = "id") %>% 
  anti_join(osa_bad_funct_code, by = "id") %>% 
  anti_join(osa_bad_account_code, by = "id")

#consolidate
osa_non_mapping <-
  list(osa_bad_fund_code, osa_bad_funct_code, osa_bad_account_code)

names(osa_non_mapping) <-
  c("osa_unmapped_fund_code",
    "osa_unmapped_funct_code",
    "osa_unmapped_account_code")


#remove objects
rm(osa_bad_fund_code,osa_bad_funct_code,osa_bad_account_code)
```
add "osa_non_mapping" to the invalid tables list
```{r}
invalid_tables <- c(invalid_tables, osa_non_mapping)
rm(osa_non_mapping)
```

## 3. LEA

### a. Enrich LEA ucoa tibble
```{r}
# This breaks out the account numbers into fund, function, and account. 
usbe_ucoa <- usbe_ucoa %>%
  mutate(
    fund                   = .[["account_number"]] %>% substr(0, 2),
    location               = .[["account_number"]] %>% substr(4, 6),
    program                = .[["account_number"]] %>%  substr(8, 11),
    funct                  = .[["account_number"]] %>%  substr(13, 16),
    object                 = .[["account_number"]] %>%  substr(18, 20),
    revenue = .[["account_number"]] %>%  substr(22, 25),
  ) %>%
  

# join the funds
left_join(
  usbe_lookup %>%
    pluck("fund") %>%
    select(
      number,
      fund_description = description,
      fund_can_submit = can_submit
    ),
  by = c("fund" = "number")
) %>%
  # join the functions
  left_join(
    usbe_lookup %>%
      pluck("location") %>%
      select(
        number,
        location_description = description,
        location_can_submit = can_submit
      ),
    by = c("location" = "number")
  ) %>%
  # join the accounts
  left_join(
    usbe_lookup %>%
      pluck("program") %>%
      select(
        number,
        program_description = description,
        program_can_submit = can_submit
      ),
    by = c("program" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("funct") %>%
      select(
        number,
        funct_description = description,
        funct_can_submit = can_submit
      ),
    by = c("funct" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("object") %>%
      select(
        number,
        object_description = description,
        object_can_submit = can_submit
      ),
    by = c("object" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("revenue") %>%
      select(
        number,
        revenue_description = description,
        revenue_can_submit = can_submit
      ),
    by = c("revenue" = "number")
  )
```

### b. Find unmapped USBE UCA
*There are many reasons why this might be the case 
**They are using an old UCOA
**They pressed the incorrect key / typos
...regardless, they must be filtered out. 

```{r}
#find wrong fund code
usbe_bad_fund_code <- usbe_ucoa %>%
  filter(!fund %in% (usbe_lookup %>%
                       pluck("fund")  %>%
                       select(number) %>%
                       unlist()))

#find wrong location code
usbe_bad_location_code<-usbe_ucoa %>%
  filter(!location %in% (usbe_lookup %>%
                        pluck("location") %>%
                        select(number) %>%
                        unlist()))
#find wrong program code
usbe_bad_program_code <- usbe_ucoa %>%
  filter(!program %in% (usbe_lookup %>%
                          pluck("program") %>%
                          select(number)   %>%
                          unlist()))

usbe_bad_funct_code <- usbe_ucoa %>%
  filter(!funct %in% (usbe_lookup %>%
                          pluck("funct") %>%
                          select(number)   %>%
                          unlist()))

usbe_bad_object_code <- usbe_ucoa %>%
  filter(!object %in% (usbe_lookup %>%
                          pluck("object") %>%
                          select(number)   %>%
                          unlist()))

usbe_bad_revenue_code <- usbe_ucoa %>%
  filter(!revenue %in% (usbe_lookup %>%
                          pluck("revenue") %>%
                          select(number)   %>%
                          unlist()))

#Remove invalid codes.
usbe_ucoa<- usbe_ucoa %>%
  anti_join(usbe_bad_fund_code, by = "id") %>%
  anti_join(usbe_bad_location_code, by = "id") %>%
  anti_join(usbe_bad_program_code, by = "id") %>%
  anti_join(usbe_bad_funct_code, by = "id") %>%
  anti_join(usbe_bad_object_code, by = "id") %>%
  anti_join(usbe_bad_revenue_code, by = "id")

#consolidate ## FIX THE NAMEING FOR THE LIST.
usbe_non_mapping <-
  list(
    usbe_unmapped_fund = usbe_bad_fund_code,
    usbe_unmapped_location= usbe_bad_location_code,
    usbe_unmapped_program= usbe_bad_program_code,
    usbe_unmapped_funct= usbe_bad_funct_code,
    usbe_unmapped_object= usbe_bad_object_code,
    usbe_unmapped_revenue= usbe_bad_revenue_code
  )

```

Remove uneeded objects
```{r}
rm(
    usbe_bad_fund_code,
    usbe_bad_location_code,
    usbe_bad_program_code,
    usbe_bad_funct_code,
    usbe_bad_object_code,
    usbe_bad_revenue_code
  )
```

```{r}
invalid_tables <- c(invalid_tables, usbe_non_mapping)
rm(usbe_non_mapping)
```

### c. check for invalid header use 
```{r}

fund_header <- usbe_ucoa %>% 
  filter(fund_can_submit != TRUE)

location_header <- usbe_ucoa %>% 
  filter(location_can_submit != TRUE)

program_header <- usbe_ucoa %>% 
  filter(program_can_submit != TRUE)

funct_header <- usbe_ucoa %>% 
  filter(funct_can_submit != TRUE)

object_header <- usbe_ucoa %>% 
  filter(object_can_submit != TRUE)

revenue_header <- usbe_ucoa %>% 
  filter(revenue_can_submit != TRUE)

usbe_ucoa <- usbe_ucoa %>% 
  anti_join(fund_header, by =c("id" = "id")) %>% 
  anti_join(location_header, by =c("id" = "id")) %>% 
  anti_join(program_header, by =c("id" = "id")) %>% 
  anti_join(funct_header, by =c("id" = "id")) %>% 
  anti_join(object_header, by =c("id" = "id")) %>% 
  anti_join(revenue_header, by =c("id" = "id"))  
  
usbe_invalid_header <- list(
  usbe_fund_header = fund_header,
  usbe_location_header = location_header,
  usbe_program_header = program_header,
  usbe_funct_header = funct_header,
  usbe_object_header = object_header,
  usbe_revenue_header = revenue_header
)
  
```

```{r}
invalid_tables <- c(invalid_tables, usbe_invalid_header)
```


```{r}
rm(
  usbe_invalid_header,
  fund_header,
  location_header,
  program_header,
  funct_header,
  object_header,
  revenue_header
)
```

Since all uca now is mapped and valid I am going to get rid of unncessary columns
```{r}

usbe_ucoa <- usbe_ucoa %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    type,
    fund,
    location,
    program,
    funct,
    object,
    revenue,
    fund_description,
    location_description,
    program_description,
    funct_description,
    object_description,
    revenue_description
  )
```


#V. Aggregate Tables

## 1. OSA

### a. By Description and Code
```{r}
agg_fund_amount <- osa_ucoa %>%
  agg_dollars_and_records(fund_description, fund)

agg_funct_amount <- osa_ucoa %>%
  agg_dollars_and_records(funct_description,funct)

agg_account_amount <- osa_ucoa %>%
  agg_dollars_and_records(account_description,account)

agg_by_description_and_code<- list(agg_fund_amount,agg_funct_amount,agg_account_amount)

names(agg_by_description_and_code) <- c("agg_fund", "agg_funct", "agg_account")

rm(agg_fund_amount,agg_funct_amount,agg_account_amount)
```

### b. By Description 
```{r}
agg_fund_amount <- osa_ucoa %>% agg_dollars_and_records(fund_description)
agg_funct_amount <- osa_ucoa %>% agg_dollars_and_records(funct_description)
agg_account_amount <- osa_ucoa %>% agg_dollars_and_records(account_description)

agg_by_description<- list(agg_fund_amount,agg_funct_amount,agg_account_amount)

names(agg_by_description) <- c("agg_fund", "agg_funct", "agg_account")

rm(agg_fund_amount,agg_funct_amount,agg_account_amount)
```

### c. By Code
```{r}
agg_fund_amount <- osa_ucoa %>% agg_dollars_and_records( fund)
agg_funct_amount <- osa_ucoa %>% agg_dollars_and_records(funct)
agg_account_amount <- osa_ucoa %>% agg_dollars_and_records(account)

agg_by_code<- list(agg_fund_amount,agg_funct_amount,agg_account_amount)

names(agg_by_code) <- c("agg_fund", "agg_funct", "agg_account")

rm(agg_fund_amount,agg_funct_amount,agg_account_amount)
```

### d. Consolidate and Remove
```{r}
#consolidate into one list

osa_agg_tables <- list(agg_by_description_and_code, agg_by_description,agg_by_code)

names(osa_agg_tables) <- c("agg_by_description_and_code",
                           "agg_by_description",
                           "agg_by_code")
#delete objects
rm(agg_by_description_and_code,agg_by_description,agg_by_code)
```



## 2. LEA

### a. By Description and Code
```{r}
agg_fund_amount <- usbe_ucoa %>%
  agg_dollars_and_records(fund_description, fund)
agg_location_amount <- usbe_ucoa %>%
  agg_dollars_and_records(location_description, location)
agg_program_amount <- usbe_ucoa %>%
  agg_dollars_and_records(program_description, program)
agg_funct_amount <- usbe_ucoa %>%
  agg_dollars_and_records(funct_description, funct)
agg_object_amount <- usbe_ucoa %>%
  agg_dollars_and_records(object_description, object)
agg_revenue_amount <- usbe_ucoa %>%
  agg_dollars_and_records(revenue_description, revenue)

agg_by_description_and_code <-
  list(
    agg_fund = agg_fund_amount,
    agg_location = agg_location_amount,
    agg_program = agg_program_amount,
    agg_funct = agg_funct_amount,
    agg_object = agg_object_amount,
    agg_revenue = agg_revenue_amount
  )

rm(
  agg_fund_amount,
  agg_location_amount,
  agg_program_amount,
  agg_funct_amount,
  agg_object_amount,
  agg_revenue_amount
)
```

### b. By Description 
```{r}
agg_fund_amount <- usbe_ucoa %>%
  agg_dollars_and_records(fund_description)
agg_location_amount <- usbe_ucoa %>%
  agg_dollars_and_records(location_description)
agg_program_amount <- usbe_ucoa %>%
  agg_dollars_and_records(program_description)
agg_funct_amount <- usbe_ucoa %>%
  agg_dollars_and_records(funct_description)
agg_object_amount <- usbe_ucoa %>%
  agg_dollars_and_records(object_description)
agg_revenue_amount <- usbe_ucoa %>%
  agg_dollars_and_records(revenue_description)

agg_by_description <-
  list(
    agg_fund = agg_fund_amount,
    agg_location = agg_location_amount,
    agg_program = agg_program_amount,
    agg_funct = agg_funct_amount,
    agg_object = agg_object_amount,
    agg_revenue = agg_revenue_amount
  )

rm(
  agg_fund_amount,
  agg_location_amount,
  agg_program_amount,
  agg_funct_amount,
  agg_object_amount,
  agg_revenue_amount
)
```

### c. By Code 
```{r}
agg_fund_amount <- usbe_ucoa %>%
  agg_dollars_and_records(fund)
agg_location_amount <- usbe_ucoa %>%
  agg_dollars_and_records(location)
agg_program_amount <- usbe_ucoa %>%
  agg_dollars_and_records(program)
agg_funct_amount <- usbe_ucoa %>%
  agg_dollars_and_records(funct)
agg_object_amount <- usbe_ucoa %>%
  agg_dollars_and_records(object)
agg_revenue_amount <- usbe_ucoa %>%
  agg_dollars_and_records(revenue)

agg_by_code <-
  list(
    agg_fund = agg_fund_amount,
    agg_location = agg_location_amount,
    agg_program = agg_program_amount,
    agg_funct = agg_funct_amount,
    agg_object = agg_object_amount,
    agg_revenue = agg_revenue_amount
  )

rm(
  agg_fund_amount,
  agg_location_amount,
  agg_program_amount,
  agg_funct_amount,
  agg_object_amount,
  agg_revenue_amount
)
```

### d. Consolidate and Remove 
```{r}
usbe_agg_tables <-
  list(
    agg_by_description_and_code = agg_by_description_and_code,
    agg_by_description = agg_by_description,
    agg_by_code = agg_by_code
  )

rm(agg_by_description_and_code, agg_by_description, agg_by_code)
```



#VI. Visualizations

I have decided to use the following colors for different uca types:

OSA = "steelblue2"
LEA = "orchid2"

## 1. OSA 


### a. Fund 
```{r}
#create a simple barplot to show the different types of ucoa codes for funds only

agg_fund_plot <-  osa_agg_tables %>%
  pluck("agg_by_description") %>%
  pluck("agg_fund") %>% 
  ggplot(aes(x = fund_description, y = total_amount)) + geom_bar(stat = "identity", fill = "steelblue2") +
  coord_flip() +
  geom_text(
    aes(label = paste0("$", total_amount)),
    hjust = -.25,
    vjust = 0,
    size = 2
  ) +
  labs(title = "Barplot of Cumulative Net Amount ($) by Description",
       x = "Description of Fund",
       y = "Cumulative Net Amount ($)")

agg_fund_plot
```


### b. Funct/Function
```{r}


temp_sequence_funct <- seq(from = 0, to = 5,  by = 1)

funct_plots<- temp_sequence_funct %>%
  map(
    barplot_description_amount,
    templist = osa_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_funct",
    uca_block = funct,
    uca_block_description = funct_description
  )

names(funct_plots) <- c("not_applicable",
                          "general_government",
                          "public_safety",
                          "public_works",
                          "health",
                          "community")

funct_plots # run funct_plots in console and view them easier than the markdown.
```


### c. Account

#### i.  Revenue
```{r}

#make plots by revenues ========================================================
temp_sequence_revenues <- seq(from = 3000, to = 3009,  by = 1)

revenue_plots<- temp_sequence_revenues %>%
  map(
    barplot_description_amount,
    templist = osa_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_account",
    uca_block = account,
    uca_block_description = account_description
  )

names(revenue_plots) <- c("revenues",
                  "taxes",
                  "licenses_and_permits",
                  "intergovernmental",
                  "charges_for_service",
                  "fines_and_forfeitures",
                  "miscellaneous",
                  "other_sources_of_funding",
                  "special_and_extraordinary_gain",
                  "suspense")
```

#### ii. Expenditures
```{r}
#Make plots for expenditures ===================================================
temp_sequence_expenditures <- seq(from = 4000, to = 4017,  by=1)

expenditure_plots<- temp_sequence_expenditures %>%
  map(
    barplot_description_amount,
    templist = osa_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_account",
    uca_block = account,
    uca_block_description = account_description
  )
names(expenditure_plots) <- c("expenditures",
                  "personnel_services",
                  "general_and_contracted_services",
                  "utilities_and_utility_services",
                  "taxes_and_fees",
                  "supplies_and_materials",
                  "grants_and_contracts",
                  "direct_payments",
                  "capital_outlays",
                  "interdepartmental_charges",
                  "judgements_and_losses",
                  "other_financing_uses",
                  "depreciation",
                  "amortiaton",
                  "bad_debt_expense",
                  "contingencies",
                  "special_and_extraordinary_loss",
                  "debt_service")

#consolidate objects
account_plots <- list(revenue_plots, expenditure_plots)
names(account_plots) <- c("revenue_plots", "expenditure_plots")

#remove redundant objects
rm(temp_sequence_revenues, temp_sequence_expenditures, revenue_plots, expenditure_plots)
```
####  iii. View
```{r}
#to see all plot simply run:
account_plots
```

To only view the revenue plots, we pluck it from the list.
```{r}
account_plots %>% pluck("revenue_plots") 
```

If you are only interested in a single plot, you need to pluck twice. shown below:
```{r}
temp <- account_plots %>% 
  pluck("expenditure_plots") %>% 
  pluck("capital_outlays")
temp
```

To access elements of the plot, use this code format. The code below selects the data frame used to generate the plot from intergovernmental revenue
```{r}
account_plots %>% 
  pluck("revenue_plots") %>%
  pluck("intergovernmental") %>%
  pluck("data")
```

##2. LEA

### a. Fund
```{r}
agg_fund_plot <-  usbe_agg_tables %>%
  pluck("agg_by_description_and_code") %>%
  pluck("agg_fund") %>% 
  ggplot(aes(x = fund_description, y = total_amount)) + geom_bar(stat = "identity", fill = "orchid2") +
  coord_flip() +
  geom_text(
    aes(label = paste0("$", total_amount)),
    hjust = -.25,
    vjust = 0,
    size = 2
  ) +
  labs(title = "Barplot of Cumulative Net Amount ($) by Description",
       x = "Description of Fund",
       y = "Cumulative Net Amount ($)")

agg_fund_plot
```
### b. Location

### c. Program
```{r}


temp_sequence <- seq(from = 0, to = 9,  by = 1)
#there is nothing in range 4000
temp_sequence <- temp_sequence[-5]


program_plots<- temp_sequence %>%
  map(
    barplot_description_amount,
    templist = usbe_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_program",
    uca_block = program,
    uca_block_description = program_description
  )

# names(funct_plots) <- c("not_applicable",
#                           "general_government",
#                           "public_safety",
#                           "public_works",
#                           "health",
#                           "community")

program_plots # run funct_plots in console and view them easier than the markdown.
```

### d. Funct/Function
```{r}


temp_sequence_funct <- seq(from = 1, to = 5,  by = 1)

funct_plots<- temp_sequence_funct %>%
  map(
    barplot_description_amount,
    templist = usbe_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_funct",
    uca_block = funct,
    uca_block_description = funct_description
  )

# names(funct_plots) <- c("not_applicable",
#                           "general_government",
#                           "public_safety",
#                           "public_works",
#                           "health",
#                           "community")

funct_plots # run funct_plots in console and view them easier than the markdown.
```

### e. object
```{r}
temp_sequence <- seq(from = 1, to = 8,  by = 1)

object_plots<- temp_sequence %>%
  map(
    barplot_description_amount,
    templist = usbe_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_object",
    uca_block = object,
    uca_block_description = object_description
  )


object_plots 
```
```{r}
object_plots %>% pluck(1) %>% pluck("data")
```

### f. revenue
right now everyone just puts in the 0000
```{r}
# temp_sequence <- seq(from = 0, to = 5,  by = 1)
# 
# revenue_plots <- temp_sequence %>%
#   map(
#     barplot_description_amount,
#     templist = usbe_agg_tables,
#     agg_by_type= "agg_by_description_and_code",
#     agg_type = "agg_revenue",
#     uca_block = revenue,
#     uca_block_description = revenue_description
#   )
# 
# 
# revenue_plots
```
#VII. Generate Invalid Report

## na_or_empty : Examine transactions with na or empty value for their account number
```{r}
invalid_tables %>% pluck("na_or_empty")
```

## invalid_length : Examine transactions with an account number too long or too small to fit either LEA or non-LEA UCOA.
```{r}
invalid_tables %>% pluck("invalid_length")
```

## invalid_lea_format : Examine transactions for LEAs with an account number with correct length, but incorrect format
```{r}
invalid_tables %>% pluck("invalid_lea_format")
```


## invalid_osa_format : Examine transactions for non LEAs with an account number with correct length, but incorrect format
```{r}
invalid_tables %>% pluck("invalid_osa_format")
```

## Unmapped codes
  * Note that for all, you can view more information. The data in each table is as follows:
    **id
    **batch_id
    **amount 
    **fiscal_year
    **account_number
    **type
    **fund
    **funct
    **...
    **fund_description
    **funct_description
    **...
### unmapped_fund_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the fund code provided does not map to the ucoa code spreadsheet
```{r}
invalid_tables %>% pluck("osa_unmapped_fund_code") %>% select(id, batch_id, amount, fund, fund_description)
```


### unmapped_fund_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the function code provided does not map to the ucoa code spreadsheet
```{r}
invalid_tables %>% pluck("osa_unmapped_funct_code") %>% select(id, batch_id, amount, funct, funct_description)
```
### unmapped_account_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet
```{r}
invalid_tables %>% pluck("osa_unmapped_account_code") %>% select(id, batch_id, amount, account, account_description)
```

### lea_unmapped_fund_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_fund") %>% select(id, batch_id, amount, fund, fund_description)
```

### lea_unmapped_location_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_location") %>% select(id, batch_id, amount, location, location_description)
```

### lea_unmapped_program_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_program") %>% select(id, batch_id, amount, program, program_description)
```

### lea_unmapped_funct_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_funct") %>% select(id, batch_id, amount, funct, funct_description)
```

### lea_unmapped_object_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_object") %>% select(id, batch_id, amount, object, object_description)
```

### lea_unmapped_revenue_classification_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_revenue") %>% select(id, batch_id, amount, revenue, revenue_description)
```



```{r}
invalid_tables %>% pluck("usbe_fund_header") %>% select(id, batch_id, amount, fund, fund_description)
```
```{r}
invalid_tables %>% pluck("usbe_location_header") %>% select(id, batch_id, amount, location, location_description)
```

```{r}
invalid_tables %>% pluck("usbe_program_header") %>% select(id, batch_id, amount, program, program_description)
```


```{r}
invalid_tables %>% pluck("usbe_funct_header") %>% select(id, batch_id, amount, funct, funct_description)
```

```{r}
invalid_tables %>% pluck("usbe_object_header") %>% select(id, batch_id, amount, object, object_description)
```


```{r}
invalid_tables %>% pluck("usbe_revenue_header") %>% select(id, batch_id, amount, revenue, revenue_description)
```

