
# 0. Program Description

**Purpose**
I am interested in learning more about how to access and pay with the UCOA codes. I decided to conduct some Exploratory Data Analysis in this document as well. This script is not really meant for a single button run-all. It rather is built to allow a data analyst to play around with the data easily. It does contain a few basic reports and interesting plots. 

Some noteworthy naming conventions:
OSA = Office of the State Auditor. It is meant to distinguish usages of the OSA's UCA code in comparison to USOE/LEA, STATE, and higher-education UCAs.

LEA = Utah State Board of Education UCA. It applies for LEA. 

DURATION: the script will take about 20-30 minutes to run.

**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "salesforce"
```

**Output(s)**


# I. Libraries and Data Sources

```{r}
#options(scipen=999)

library(lubridate)
library(magrittr)
library(odbc)
library(readxl) 
library(tidyverse)
library(stringi) 
library(tidyr)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)

rm(dsn_aws, dsn_salesforce)

```

## stuff for parellel processing
```{r}
# library(parallel)
# numCores <- detectCores()
# numCores
# 
# cl <- makeCluster(numCores)
# 
# x<-1
# clusterExport(cl, "x")
# clusterEvalQ(cl, x)
# 
# 
# clusterEvalQ(cl, {
#   library(ggplot2)
#   library(stringr)
# })
```


# II. Function Definitions

## 1. agg_dollars_and_records
```{r}
agg_dollars_and_records<- function(df, ...){
  # Purpose: groups the data by supplied grouping variables, and aggregates the
  # date to have a total dollar amount and a count for the number of transactions
  # with such variables. Basically this will group uca codings into dollar and
  # frequency amounts. Two metrics of interest to Alex.
  #
  # Inputs: *df (tibble or dataframe): a dataframe which has the grouping variables. it should have an amount column
  #         *... : the grouping variables. should be a uca field.
  # Outputs: tibble :an aggregated tibble
  
  grouping_vars <- enquos(...)
  
  agg_table <- df %>% 
    group_by(!!! grouping_vars) %>% 
    summarize(total_amount = sum(amount),
              num_of_trans = n()) %>% 
    arrange(desc(total_amount))
  
}
```


```{r}
barplot_amount <- function(templist,agg_by_type, agg_type, uca_block, temprange){
  # Description
  # 
  # Inputs: templist (list):
  #         agg_by_type(string/char):  used to decide whether to pluck by_description_and_code, by_description, or by_code
  #         agg_type(string/char): used to pluck a specific type of aggregat table such as agg_fund or agg_function
  #         uca_block(object?): the uca block of interest, ex: fund, location, object...
  #         temprange(int): a range of interest. for example : 4000 ==> 40000000
  # 
  # Outputs:
  #         p (ggplot object)
  
  uca_block <-enquo(uca_block)
  
  p <- templist %>%
    pluck(agg_by_type) %>%
    pluck(agg_type) %>%
    filter(str_detect(!!uca_block, paste0("^", temprange))) %>%
    ggplot(aes(x = !!uca_block, y = total_amount)) +
    geom_bar(stat = "identity", fill = "lightcoral") +
    coord_flip() +
    geom_text(
      aes(label = paste0("$", total_amount)),
      hjust = "inward",#-.25,
      vjust = "inwward",#0,
      size = 3
    ) +
    labs(title = paste0(
      "barplot of ",
      rlang::as_name(uca_block),
      " starting with: ",
      temprange
    ))
  p

}

```


```{r}
barplot_description_amount <- function(templist,agg_by_type, agg_type,uca_block, uca_block_description, temprange){
  # Description
  # 
  # Inputs: templist (list):
  #         agg_by_type(string/char):  used to decide whether to pluck by_description_and_code, by_description, or by_code
  #         agg_type(string/char): used to pluck a specific type of aggregat table such as agg_fund or agg_function
  #         uca_block(object?): the uca block of interest, ex: fund, location, object...
  #         temprange(int): a range of interest. for example : 4000 ==> 40000000
  # 
  # Outputs:
  #         p (ggplot object)
  uca_block <-enquo(uca_block)
  uca_block_description <-enquo(uca_block_description)
  
  p <- templist %>%
    pluck(agg_by_type) %>%
    pluck(agg_type) %>%
    filter(str_detect(!!uca_block, paste0("^", temprange))) %>%
    ggplot(aes(x = !!uca_block_description, y = total_amount)) +
    geom_bar(stat = "identity", fill = "steelblue2") +
    coord_flip() +
    geom_text(
      aes(label = paste0("$", total_amount)),
      hjust = "inward",#-.25,
      vjust = "inwward",#0,
      size = 3
    ) +
    labs(title = paste0(
      "barplot of ",
      rlang::as_name(uca_block_description),
      " starting with: ",
      temprange
    ))
  p

}


```

# III. LOAD, QUERY, and WRANGLE

## 1. OSA

```{r}
osa_file_name <- "ucoa.xlsx"

# fund =========================================================================
osa_fund <-
  read_xlsx(osa_file_name, sheet = excel_sheets(osa_file_name)[[1]]) %>%
  mutate(number = number %>% str_pad(3, pad = "0")) %>% 
  mutate(level_primary = 
           ifelse(
             str_detect(full_description, "^(.*)[:space:]-[:space:]"),
             stri_extract_first(full_description, regex = "^(.*)[:space:]-[:space:]"),
             full_description
           ), 
         level_secondary = stri_extract_first(full_description, regex = "[:space:]-[:space:](.*)$"),
         level_primary = str_replace(level_primary,"-","") %>% str_trim(),
         level_secondary = str_replace(level_secondary,"-","") %>% str_trim())


# add additional fund numbers.
extra_fund_numbers <-
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    short_description = NA,
    full_description = case_when(
      number %in% (202:298) ~ "Special Revenue Funds (as assigned by local government)",
      number %in% (302:398) ~ "Debt Service Funds (as assigned by local government)",
      number %in% (402:448) ~ "Capital Projects Funds (as assigned by local government)",
      number %in% (452:498) ~ "Permanent Funds (as assigned by local government)",
      number %in% (502:598) ~ "Enterprise Funds (as assigned by local government)",
      number %in% (602:698) ~ "Internal Service Funds (as assigned by local government)",
      number %in% (702:798) ~ "Trust and Agency Funds (as assigned by local government)"
    ),
    detail = NA,
    level_primary = case_when(
      number %in% (202:298) ~ "Special Revenue Funds",
      number %in% (302:398) ~ "Debt Service Funds",
      number %in% (402:448) ~ "Capital Projects Funds ",
      number %in% (452:498) ~ "Permanent Funds",
      number %in% (502:598) ~ "Enterprise Funds",
      number %in% (602:698) ~ "Internal Service Funds",
      number %in% (702:798) ~ "Trust and Agency Funds"
    ),
    level_secondary = paste(level_primary,str_extract(number, "[:digit:][:digit:]$"))
  )


osa_fund <-
  osa_fund %>%
  bind_rows(extra_fund_numbers) %>%
  mutate(code_primary = str_sub(number, 0, 2),
         code_secondary = str_sub(number, 2, 3)) %>%
  select(number,
         description = full_description,
         code_primary,
         code_secondary,
         level_primary,
         level_secondary)

# funct ========================================================================
osa_funct <-
  read_xlsx(osa_file_name, sheet = excel_sheets(osa_file_name)[[2]])

# quicker than str_pad to the entire column
osa_funct$number[[1]] <- "000000"

osa_funct<- osa_funct %>% 
  mutate(number = as.character(number),
         code_primary = str_sub(number,0,2),
         code_secondary = str_sub(number,3,4),
         code_tertiary= str_sub(number,5,6),
         temp_description = full_description) %>% 
         separate(temp_description,
                  into = c("level_primary","level_secondary","level_tertiary"),
                  sep= "[:space:]-[:space:]") %>% 
  select(-short_description, -detail) %>% 
  rename( description = full_description)




# account ======================================================================
osa_account <-
  read_xlsx(osa_file_name, sheet = excel_sheets(osa_file_name)[[3]]) %>%
  mutate(number = as.character(number),
         code_primary = str_sub(number,0,4),
         code_secondary = str_sub(number,5,6),
         code_tertiary= str_sub(number,7,8),
         temp_description = full_description) %>% 
         separate(temp_description,
                  into = c("level_primary","level_secondary","level_tertiary"),
                  sep= "[:space:]-[:space:]") %>% 
  select(-short_description, -detail) %>% 
  rename( description = full_description)


# consolidate ==================================================================
osa_lookup <-
  list(fund        = osa_fund,
       funct       = osa_funct,
       account     = osa_account)

```
Remove unneeded objects
```{r}
rm(osa_fund, osa_funct, osa_account, extra_fund_numbers , osa_file_name)
```


## 2. USBE
```{r}
# fund =========================================================================
usbe_file_name <- "FY20 COA-USBE.xlsx"

usbe_fund <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[1]]) %>% 
  rename(number = FundCode,
         description = FundDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

##add back the ranges
extra_fund_numbers <- c(27:29, 61:69) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    description =
      case_when(
        number %in% (27:29) ~ "Special Revenue Funds - (Assigned by District)",
        number %in% (61:69) ~ "Interal Service Fund - (Assigned by District)"
      ),
    can_submit = TRUE
  )

usbe_fund <-
  usbe_fund %>%
  bind_rows(extra_fund_numbers)

# Location =====================================================================   
usbe_location<- c(0:499,600:999) %>%
  # str_pad(3, pad = "0") %>% 
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
    mutate( description =
      case_when(
        as.numeric(number) <= 10    ~ "Pre School",
        as.numeric(number) >= 11 & as.numeric(number) <= 99   ~ "District Level",
        number %in% (100:299) ~ "Elementary Schools",
        number %in% (300:399) ~ "Middle Schools",
        number %in% (400:499) ~ "Junior High Schools/Middle Schools",
        number %in% (600:699) ~ "Special Schools, Secondary",
        number %in% (700:799) ~ "High Schools",
        number %in% (800:899) ~ "Special Schools, Elementary",
        number %in% (900:975) ~ "Private Schools",
        number %in% (976:999) ~ "Adult Education Schools"
      ),
      can_submit = TRUE
      ) %>% 
  mutate(number = number %>% str_pad(3, pad = "0")) 
  

# program  =====================================================================
usbe_program <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[2]]) %>%
  rename(number = ProgramCode,
         description = ProgramDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = number %>% str_pad(4, pad = "0"))

extra_program_numbers <- c(
  2000:3699,
  # 2000 SCHOOL LEVEL PROGRAMS
  5251:5290,
  7804:7809,
  7811:7819,
  7821:7829,
  7831:7839,
  7841:7849,
  7851:7859,
  7871:7879,
  7891:7899,
  7916:7919,
  7911:7914,
  7921:7929,
  7931:7939,
  7941:7949,
  7951:7959
) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    description =
      case_when(
        number %in% (2000:2099) ~ "General School",
        number %in% (2100:2199) ~ "General Studentbody",
        number %in% (2200:3299) ~ "Instructional Classes",
        number %in% (3300:3599) ~ "Other Instructional Classes",
        number %in% (3600:3699) ~ "Student Activity Funds",
        
        number %in% (5251:5259) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        number %in% (5260:5269) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        number %in% (5270:5290) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        
        number %in% (7804:7809) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7811:7819) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7821:7829) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7831:7839) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7841:7849) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7851:7859) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7871:7879) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7891:7899) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7916:7919) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7911:7914) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7921:7929) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7931:7939) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7941:7949) ~ "(NCLB) Numbers reserved for districts",
        number %in% (7951:7959) ~ "(NCLB) Numbers reserved for districts"
      ),
    can_submit = TRUE
  )

usbe_program <-
  usbe_program %>%
  bind_rows(extra_program_numbers)  

# Function =====================================================================
usbe_funct <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[4]]) %>%
  rename(number = FunctionCode,
         description = FunctionDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

# Object =======================================================================

usbe_object <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[5]]) %>%
  rename(number = ObjectCode,
         description = ObjectDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

# Revenue Classification" ======================================================
usbe_revenue <-
  read_xlsx(usbe_file_name, sheet = excel_sheets(usbe_file_name)[[3]]) %>%
  rename(number = RevenueCode,
         description = RevenueDescription,
         can_submit = CanSubmit) %>% 
  mutate(number = as.character(number))

# Many LEA put 0000 for their revenue code. To keep them from all being removed,
# I created a temporary holder. I will likely change the name once I understand
# why this code is always being used.
extra_revenue_numbers <- c("0000") %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("number" = "value") %>%
  mutate(
    description =
      case_when(number == "0000" ~ "TEMPORARY HOLDER - ALEX NIELSON",),
    can_submit = TRUE
  )

usbe_revenue <-
  usbe_revenue %>%
  bind_rows(extra_revenue_numbers)


#consolidate ===================================================================
usbe_lookup <- list(
  fund     = usbe_fund,
  location = usbe_location,
  program  = usbe_program,
  funct    = usbe_funct,
  object   = usbe_object,
  revenue  = usbe_revenue
)

```
Remove unneeded objects
```{r}
rm(
  usbe_fund,
  usbe_location,
  usbe_funct,
  usbe_program,
  usbe_revenue,
  usbe_object,
  extra_program_numbers,
  extra_fund_numbers,
  extra_revenue_numbers,
  usbe_file_name
)
```



#IV. Load and Validate UCA codes
 *We will vadidate the code to remove missing values, and "". Then generate for three main reports. The first report contains both invalid LEA and NON-LEA codes. THe second report will be valid LEA codes (lea_reported_ucoa). The third report will be valid NON-LEA codes (I call it osa_reported_ucoa)

## 1. Query AWS transaction table
```{r}

# 1. Query the database, get all the records that are not obviously missing data. 
reported_ucoa <-
dbGetQuery(
  odbc_aws,
  paste("
        SELECT id, 
        batch_id,
        amount,
        fiscal_year,
        account_number,
        type
        FROM transaction
        WHERE fiscal_year = 2019 
        AND account_number IS NOT NULL 
        LIMIT 1000000")) %>% # note I am limitingto 10000000 so it doesn't take an eternity.
as_tibble() 

# 2. double check for NA or "" -------------------------------------------------

invalid_reported_na_or_empty <- reported_ucoa %>%
  filter(account_number == "",
        is.na(account_number))

reported_ucoa <- 
  reported_ucoa %>% 
  filter(account_number != "", !is.na(account_number))

# 3. check correct length ------------------------------------------------------

# 19 is for normal, 25 is for USBE (dashes are included in string legth)
invalid_ucoa_length <- reported_ucoa %>% 
  filter(nchar(account_number) != 19 && nchar(account_number)!= 25) %>% 
  mutate(account_number_length = nchar(account_number),
         reason = case_when(
          account_number_length < 19 ~ "uca code too short for non LEA",
          account_number_length > 19 & account_number_length<25 ~ "uca code incorrect length",
          account_number_length > 25 ~ "uca code too long for LEA"))

reported_ucoa <- reported_ucoa %>% 
  filter(nchar(account_number) == 19 || nchar(account_number)== 25)


# 4. partition out queried set into OSA and USBE subsets -----------------------

# a. filter for only lea
usbe_reported_ucoa <- reported_ucoa %>% filter(nchar(account_number)== 25)

# b. filter for non USBE
osa_reported_ucoa <- reported_ucoa %>% filter(nchar(account_number)== 19)

# USBE validation ==============================================================

# check for valid form. ie: ##-###-####-####-###-#### 
 
invalid_usbe_ucoa_code <-
  usbe_reported_ucoa %>%
  filter(!str_detect(
    .$account_number,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))

usbe_reported_ucoa <-
  usbe_reported_ucoa %>%
  filter(str_detect(
    .$account_number,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))

# OSA validation================================================================ 

# check if the codes are valid form. ie: ###-######-########  

invalid_osa_ucoa_codes <- osa_reported_ucoa %>%
  filter(!str_detect(
    .$account_number,
    regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")
  ))

osa_reported_ucoa <-
  osa_reported_ucoa %>%
  filter(str_detect(
    .$account_number,
    regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")
  ))

# consolidate ==================================================================
osa_ucoa <- osa_reported_ucoa
usbe_ucoa <- usbe_reported_ucoa
invalid_tables <-
  list(invalid_reported_na_or_empty,
       invalid_ucoa_length,
       invalid_usbe_ucoa_code,
       invalid_osa_ucoa_codes)
names(invalid_tables) <- c("na_or_empty",
                           "invalid_length",
                           "invalid_lea_format",
                           "invalid_osa_format")

# remove unneeded objects ======================================================
# comment any object that you want to inspect in the global environment pane
rm(
  invalid_reported_na_or_empty,
  invalid_usbe_ucoa_code,
  invalid_osa_ucoa_codes,
  invalid_ucoa_length,
  osa_reported_ucoa,
  usbe_reported_ucoa,
  reported_ucoa
)
  
```

Now that the queried data is in a useful and valid form, we must ensure that the uca correctly maps. The processes for this is as follows: First, we enrich the tables by atomizing the uca block. Then we join off the lookup tables made above. Then we find those without descriptions and save them to invalid tables. Finally we anti-join them from the original query so that visualizations and valid aggregations can be made.


##2. OSA 

### a. Enrich OSA 
```{r}
# This breaks out the account numbers into fund, function, and account. 
osa_ucoa <- osa_ucoa%>% 
  mutate(
    fund = .[["account_number"]] %>% substr(0, 3),
    funct = .[["account_number"]] %>% substr(5, 10),
    account = .[["account_number"]] %>%  substr(12, 19),
    fund_code_primary = str_sub(fund,0,2),
    fund_code_secondary = str_sub(fund,2,3),
    funct_code_primary = str_sub(funct,0,2),
    funct_code_secondary = str_sub(funct,3,4),
    funct_code_tertiary = str_sub(funct,5,6),
    account_code_primary = str_sub(account,0,4),
    account_code_secondary = str_sub(account,5,6),
    account_code_tertiary = str_sub(account,7,8)
  ) %>% 

# Now we need to join ucoa.xlsx, so we know what the codes mean.

  # join the funds
  left_join(
    osa_lookup %>%
      pluck("fund") %>%
      as_tibble() %>%
      select(
        number,
        fund_description = description,
        #lu_fund_code_primary = code_primary,
        #lu_fund_code_secondary = code_secondary,
        fund_level_primary = level_primary,
        fund_level_secondary = level_secondary
      ),
    by = c("fund" = "number")
  ) %>%
  # join the functions
  left_join(
    osa_lookup %>%
      pluck("funct") %>%
      as_tibble() %>%
      select(
        number,
        funct_description = description,
        #lu_funct_code_primary = code_primary,
        #lu_funct_code_secondary = code_secondary,
        #lu_funct_code_tertiary = code_tertiary,
        funct_level_primary = level_primary,
        funct_level_secondary = level_secondary,
        funct_level_tertiary = level_tertiary
      ),
    by = c("funct" = "number")
  ) %>%
  # join the accounts
  left_join(
    osa_lookup %>%
      pluck("account") %>%
      as_tibble() %>%
      select(
        number,
        account_description = description,
        #lu_account_code_primary = code_primary,
        #lu_account_code_secondary = code_secondary,
        #lu_account_code_tertiary = code_tertiary,
        account_level_primary = level_primary,
        account_level_secondary = level_secondary,
        account_level_tertiary = level_tertiary
      ),
    by = c("account" = "number")
  )
```
### b. Find unmapped UCA
*There are many reasons why this might be the case 
**They are using an old UCOA
**They pressed the incorrect key / typos
...regardless, they must be filtered out. 

```{r}
#find wrong fund code
osa_bad_fund_code <- osa_ucoa %>%
  filter(!fund %in% (osa_lookup %>%
                       pluck("fund")  %>%
                       select(number) %>%
                       unlist()))
  #check primary
osa_bad_fund_code_primary <- osa_ucoa %>%
  filter(!fund_code_primary %in% (osa_lookup %>%
                       pluck("fund")  %>%
                       select(code_primary) %>%
                       unlist()))
  #check secondary
osa_bad_fund_code_secondary <- osa_ucoa %>%
  filter(!fund_code_secondary %in% (osa_lookup %>%
                       pluck("fund")  %>%
                       select(code_secondary) %>%
                       unlist()))

#find wrong function code
osa_bad_funct_code<-osa_ucoa %>%
  filter(!funct %in% (osa_lookup %>%
                        pluck("funct") %>%
                        select(number) %>%
                        unlist()))

osa_bad_account_code <- osa_ucoa %>%
  filter(!account %in% (osa_lookup %>%
                          pluck("account") %>%
                          select(number)   %>%
                          unlist()))


#now remove incorrectly mapped. we will save them to report, but do not want
#them in our analysis.
osa_ucoa<- osa_ucoa %>% 
  anti_join(osa_bad_fund_code, by = "id") %>% 
  anti_join(osa_bad_funct_code, by = "id") %>% 
  anti_join(osa_bad_account_code, by = "id")

#consolidate
osa_non_mapping <-
  list(osa_bad_fund_code, osa_bad_funct_code, osa_bad_account_code)

names(osa_non_mapping) <-
  c("osa_unmapped_fund_code",
    "osa_unmapped_funct_code",
    "osa_unmapped_account_code")


#remove objects
rm(osa_bad_fund_code,osa_bad_funct_code,osa_bad_account_code)
```

### c. Examine Atomic UCA
```{r}
funct_error <- osa_non_mapping %>%
  pluck("osa_unmapped_funct_code") %>%
  left_join(
    osa_lookup %>%
      pluck("funct") %>%
      select(code_primary,
             funct_level_primary_atom = level_primary) %>%
      distinct() %>%
      unnest()
    ,
    by = c("funct_code_primary" = "code_primary")
  ) %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    funct,
    funct_code_primary,
    funct_code_secondary,
    funct_code_tertiary,
    funct_description,
    funct_level_primary_atom
  )

invalid_primary_code <- funct_error %>% 
  filter(funct_level_primary_atom %>% is.na())

funct_error <-
  funct_error %>% anti_join(invalid_primary_code, by = c("id" = "id"))


funct_error2 <- funct_error %>%
  left_join(
    osa_lookup %>%
      pluck("funct") %>%
      select(code_primary,
             code_secondary,
             funct_level_secondary_atom = level_secondary) %>%
      distinct() %>%
      unnest()
    ,
    by = c(
      "funct_code_primary" = "code_primary",
      "funct_code_secondary" = "code_secondary"
    )
  ) %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    funct,
    funct_code_primary,
    funct_code_secondary,
    funct_code_tertiary,
    funct_description,
    funct_level_primary_atom,
    funct_level_secondary_atom
  )

invalid_secondary_code <- funct_error2 %>% 
  filter(funct_level_secondary_atom %>% is.na())


invalid_tertiary_code <-
  funct_error2 %>% anti_join(invalid_secondary_code, by = c("id" = "id"))


funct_invalid_code <- list(
  invalid_primary_code = invalid_primary_code,
  invalid_secondary_code = invalid_secondary_code,
  invalid_tertiary_code = invalid_tertiary_code
)

remove(funct_error,funct_error2, invalid_primary_code,invalid_secondary_code,invalid_tertiary_code)

```

check the account atomized levels
```{r}
account_error <- osa_non_mapping %>%
  pluck("osa_unmapped_account_code") %>%
  left_join(
    osa_lookup %>%
      pluck("account") %>%
      select(code_primary,
             account_level_primary_atom = level_primary) %>%
      distinct() %>%
      unnest()
    ,
    by = c("account_code_primary" = "code_primary")
  ) %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    account,
    account_code_primary,
    account_code_secondary,
    account_code_tertiary,
    account_description,
    account_level_primary_atom
  )

invalid_primary_code <- account_error %>% 
  filter(account_level_primary_atom %>% is.na())

account_error <-
  account_error %>% anti_join(invalid_primary_code, by = c("id" = "id"))


account_error2 <- account_error %>%
  left_join(
    osa_lookup %>%
      pluck("account") %>%
      select(code_primary,
             code_secondary,
             account_level_secondary_atom = level_secondary) %>%
      distinct() %>%
      unnest()
    ,
    by = c(
      "account_code_primary" = "code_primary",
      "account_code_secondary" = "code_secondary"
    )
  ) %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    account,
    account_code_primary,
    account_code_secondary,
    account_code_tertiary,
    account_description,
    account_level_primary_atom,
    account_level_secondary_atom
  )

invalid_secondary_code <- account_error2 %>% 
  filter(account_level_secondary_atom %>% is.na())


invalid_tertiary_code <-
 account_error2 %>% anti_join(invalid_secondary_code, by = c("id" = "id"))


account_invalid_code <- list(
  invalid_primary_code = invalid_primary_code,
  invalid_secondary_code = invalid_secondary_code,
  invalid_tertiary_code = invalid_tertiary_code
)

remove(account_error,account_error2, invalid_primary_code,invalid_secondary_code,invalid_tertiary_code)

```

add "osa_non_mapping" to the invalid tables list
```{r}
invalid_tables <- c(invalid_tables, osa_non_mapping)
rm(osa_non_mapping)
```

## 3. USBE

### a. Enrich USBE
```{r}
# This breaks out the account numbers into fund, function, and account. 
usbe_ucoa <- usbe_ucoa %>%
  mutate(
    fund                   = .[["account_number"]] %>% substr(0, 2),
    location               = .[["account_number"]] %>% substr(4, 6),
    program                = .[["account_number"]] %>%  substr(8, 11),
    funct                  = .[["account_number"]] %>%  substr(13, 16),
    object                 = .[["account_number"]] %>%  substr(18, 20),
    revenue = .[["account_number"]] %>%  substr(22, 25),
  ) %>%
  

# join the funds
left_join(
  usbe_lookup %>%
    pluck("fund") %>%
    select(
      number,
      fund_description = description,
      fund_can_submit = can_submit
    ),
  by = c("fund" = "number")
) %>%
  # join the functions
  left_join(
    usbe_lookup %>%
      pluck("location") %>%
      select(
        number,
        location_description = description,
        location_can_submit = can_submit
      ),
    by = c("location" = "number")
  ) %>%
  # join the accounts
  left_join(
    usbe_lookup %>%
      pluck("program") %>%
      select(
        number,
        program_description = description,
        program_can_submit = can_submit
      ),
    by = c("program" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("funct") %>%
      select(
        number,
        funct_description = description,
        funct_can_submit = can_submit
      ),
    by = c("funct" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("object") %>%
      select(
        number,
        object_description = description,
        object_can_submit = can_submit
      ),
    by = c("object" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("revenue") %>%
      select(
        number,
        revenue_description = description,
        revenue_can_submit = can_submit
      ),
    by = c("revenue" = "number")
  )
```

### b. Find unmapped UCA
*There are many reasons why this might be the case 
**They are using an old UCOA
**They pressed the incorrect key / typos
...regardless, they must be filtered out. 

```{r}
#find wrong fund code
usbe_bad_fund_code <- usbe_ucoa %>%
  filter(!fund %in% (usbe_lookup %>%
                       pluck("fund")  %>%
                       select(number) %>%
                       unlist()))

#find wrong location code
usbe_bad_location_code<-usbe_ucoa %>%
  filter(!location %in% (usbe_lookup %>%
                        pluck("location") %>%
                        select(number) %>%
                        unlist()))
#find wrong program code
usbe_bad_program_code <- usbe_ucoa %>%
  filter(!program %in% (usbe_lookup %>%
                          pluck("program") %>%
                          select(number)   %>%
                          unlist()))

usbe_bad_funct_code <- usbe_ucoa %>%
  filter(!funct %in% (usbe_lookup %>%
                          pluck("funct") %>%
                          select(number)   %>%
                          unlist()))

usbe_bad_object_code <- usbe_ucoa %>%
  filter(!object %in% (usbe_lookup %>%
                          pluck("object") %>%
                          select(number)   %>%
                          unlist()))

usbe_bad_revenue_code <- usbe_ucoa %>%
  filter(!revenue %in% (usbe_lookup %>%
                          pluck("revenue") %>%
                          select(number)   %>%
                          unlist()))

#Remove invalid codes.
usbe_ucoa<- usbe_ucoa %>%
  anti_join(usbe_bad_fund_code, by = "id") %>%
  anti_join(usbe_bad_location_code, by = "id") %>%
  anti_join(usbe_bad_program_code, by = "id") %>%
  anti_join(usbe_bad_funct_code, by = "id") %>%
  anti_join(usbe_bad_object_code, by = "id") %>%
  anti_join(usbe_bad_revenue_code, by = "id")

#consolidate ## FIX THE NAMEING FOR THE LIST.
usbe_non_mapping <-
  list(
    usbe_unmapped_fund = usbe_bad_fund_code,
    usbe_unmapped_location= usbe_bad_location_code,
    usbe_unmapped_program= usbe_bad_program_code,
    usbe_unmapped_funct= usbe_bad_funct_code,
    usbe_unmapped_object= usbe_bad_object_code,
    usbe_unmapped_revenue= usbe_bad_revenue_code
  )

```

Remove uneeded objects
```{r}
rm(
    usbe_bad_fund_code,
    usbe_bad_location_code,
    usbe_bad_program_code,
    usbe_bad_funct_code,
    usbe_bad_object_code,
    usbe_bad_revenue_code
  )
```

```{r}
invalid_tables <- c(invalid_tables, usbe_non_mapping)
rm(usbe_non_mapping)
```

### c. Check for invalid header use 
entites which report using the USBE uca cannot use the header code number. the usbe gave me a document with a field called can_submit which essentially was a boolean for whether a code was or was not a header code. 
```{r}

fund_header <- usbe_ucoa %>% 
  filter(fund_can_submit != TRUE)

location_header <- usbe_ucoa %>% 
  filter(location_can_submit != TRUE)

program_header <- usbe_ucoa %>% 
  filter(program_can_submit != TRUE)

funct_header <- usbe_ucoa %>% 
  filter(funct_can_submit != TRUE)

object_header <- usbe_ucoa %>% 
  filter(object_can_submit != TRUE)

revenue_header <- usbe_ucoa %>% 
  filter(revenue_can_submit != TRUE)

usbe_ucoa <- usbe_ucoa %>% 
  anti_join(fund_header, by =c("id" = "id")) %>% 
  anti_join(location_header, by =c("id" = "id")) %>% 
  anti_join(program_header, by =c("id" = "id")) %>% 
  anti_join(funct_header, by =c("id" = "id")) %>% 
  anti_join(object_header, by =c("id" = "id")) %>% 
  anti_join(revenue_header, by =c("id" = "id"))  
  
# consolidate
usbe_invalid_header <- list(
  usbe_fund_header = fund_header,
  usbe_location_header = location_header,
  usbe_program_header = program_header,
  usbe_funct_header = funct_header,
  usbe_object_header = object_header,
  usbe_revenue_header = revenue_header
)
  
```

consolidate the invalid header usage into the invalid tables object
```{r}
invalid_tables <- c(invalid_tables, usbe_invalid_header)
```

Remove objects
```{r}
rm(
  usbe_invalid_header,
  fund_header,
  location_header,
  program_header,
  funct_header,
  object_header,
  revenue_header
)
```

Since all uca now is mapped and valid I am going to get rid of unncessary columns
```{r}

usbe_ucoa <- usbe_ucoa %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    type,
    fund,
    location,
    program,
    funct,
    object,
    revenue,
    fund_description,
    location_description,
    program_description,
    funct_description,
    object_description,
    revenue_description
  )
```


#V. Aggregate Tables
This section was created for two reasons 1) Provide a reference to common and interesting aggregations. These are all possibly report worthy in my opinion 2) To make visualization code run much faster, since the aggregation does not need to be calculated for each plot, it can just sit in memory, and the visualizations can simply reference the aggregation. 

## 1. OSA

### a. By Description and Code
```{r}
agg_fund_amount <- osa_ucoa %>%
  agg_dollars_and_records(fund_description, fund)

agg_funct_amount <- osa_ucoa %>%
  agg_dollars_and_records(funct_description,funct)

agg_account_amount <- osa_ucoa %>%
  agg_dollars_and_records(account_description,account)

agg_by_description_and_code<- list(agg_fund_amount,agg_funct_amount,agg_account_amount)

names(agg_by_description_and_code) <- c("agg_fund", "agg_funct", "agg_account")

rm(agg_fund_amount,agg_funct_amount,agg_account_amount)
```

### b. By Description 
```{r}
agg_fund_amount <- osa_ucoa %>% agg_dollars_and_records(fund_description)
agg_funct_amount <- osa_ucoa %>% agg_dollars_and_records(funct_description)
agg_account_amount <- osa_ucoa %>% agg_dollars_and_records(account_description)

agg_by_description<- list(agg_fund_amount,agg_funct_amount,agg_account_amount)

names(agg_by_description) <- c("agg_fund", "agg_funct", "agg_account")

rm(agg_fund_amount,agg_funct_amount,agg_account_amount)
```

### c. By Code
```{r}
agg_fund_amount <- osa_ucoa %>% agg_dollars_and_records( fund)
agg_funct_amount <- osa_ucoa %>% agg_dollars_and_records(funct)
agg_account_amount <- osa_ucoa %>% agg_dollars_and_records(account)

agg_by_code<- list(agg_fund_amount,agg_funct_amount,agg_account_amount)

names(agg_by_code) <- c("agg_fund", "agg_funct", "agg_account")

rm(agg_fund_amount,agg_funct_amount,agg_account_amount)
```

### d. Consolidate and Remove
```{r}
#consolidate into one list

osa_agg_tables <- list(agg_by_description_and_code, agg_by_description,agg_by_code)

names(osa_agg_tables) <- c("agg_by_description_and_code",
                           "agg_by_description",
                           "agg_by_code")
#delete objects
rm(agg_by_description_and_code,agg_by_description,agg_by_code)
```



## 2. USBE

### a. By Description and Code
```{r}
agg_fund_amount <- usbe_ucoa %>%
  agg_dollars_and_records(fund_description, fund)
agg_location_amount <- usbe_ucoa %>%
  agg_dollars_and_records(location_description, location)
agg_program_amount <- usbe_ucoa %>%
  agg_dollars_and_records(program_description, program)
agg_funct_amount <- usbe_ucoa %>%
  agg_dollars_and_records(funct_description, funct)
agg_object_amount <- usbe_ucoa %>%
  agg_dollars_and_records(object_description, object)
agg_revenue_amount <- usbe_ucoa %>%
  agg_dollars_and_records(revenue_description, revenue)

agg_by_description_and_code <-
  list(
    agg_fund = agg_fund_amount,
    agg_location = agg_location_amount,
    agg_program = agg_program_amount,
    agg_funct = agg_funct_amount,
    agg_object = agg_object_amount,
    agg_revenue = agg_revenue_amount
  )

rm(
  agg_fund_amount,
  agg_location_amount,
  agg_program_amount,
  agg_funct_amount,
  agg_object_amount,
  agg_revenue_amount
)
```

### b. By Description 
```{r}
agg_fund_amount <- usbe_ucoa %>%
  agg_dollars_and_records(fund_description)
agg_location_amount <- usbe_ucoa %>%
  agg_dollars_and_records(location_description)
agg_program_amount <- usbe_ucoa %>%
  agg_dollars_and_records(program_description)
agg_funct_amount <- usbe_ucoa %>%
  agg_dollars_and_records(funct_description)
agg_object_amount <- usbe_ucoa %>%
  agg_dollars_and_records(object_description)
agg_revenue_amount <- usbe_ucoa %>%
  agg_dollars_and_records(revenue_description)

agg_by_description <-
  list(
    agg_fund = agg_fund_amount,
    agg_location = agg_location_amount,
    agg_program = agg_program_amount,
    agg_funct = agg_funct_amount,
    agg_object = agg_object_amount,
    agg_revenue = agg_revenue_amount
  )

rm(
  agg_fund_amount,
  agg_location_amount,
  agg_program_amount,
  agg_funct_amount,
  agg_object_amount,
  agg_revenue_amount
)
```

### c. By Code 
```{r}
agg_fund_amount <- usbe_ucoa %>%
  agg_dollars_and_records(fund)
agg_location_amount <- usbe_ucoa %>%
  agg_dollars_and_records(location)
agg_program_amount <- usbe_ucoa %>%
  agg_dollars_and_records(program)
agg_funct_amount <- usbe_ucoa %>%
  agg_dollars_and_records(funct)
agg_object_amount <- usbe_ucoa %>%
  agg_dollars_and_records(object)
agg_revenue_amount <- usbe_ucoa %>%
  agg_dollars_and_records(revenue)

agg_by_code <-
  list(
    agg_fund = agg_fund_amount,
    agg_location = agg_location_amount,
    agg_program = agg_program_amount,
    agg_funct = agg_funct_amount,
    agg_object = agg_object_amount,
    agg_revenue = agg_revenue_amount
  )

rm(
  agg_fund_amount,
  agg_location_amount,
  agg_program_amount,
  agg_funct_amount,
  agg_object_amount,
  agg_revenue_amount
)
```

### d. Consolidate and Remove 
```{r}
usbe_agg_tables <-
  list(
    agg_by_description_and_code = agg_by_description_and_code,
    agg_by_description = agg_by_description,
    agg_by_code = agg_by_code
  )

rm(agg_by_description_and_code, agg_by_description, agg_by_code)
```



#VI. Visualizations

I have decided to use the following colors for different uca types:

## 1. OSA 


### a. Fund 
```{r}
#create a simple barplot to show the different types of ucoa codes for funds only

agg_fund_plot <-  osa_agg_tables %>%
  pluck("agg_by_description") %>%
  pluck("agg_fund") %>% 
  ggplot(aes(x = fund_description, y = total_amount)) + geom_bar(stat = "identity", fill = "steelblue2") +
  coord_flip() +
  geom_text(
    aes(label = paste0("$", total_amount)),
    hjust = "inward",
    vjust = .1,
    size = 2
  ) +
  labs(title = "Barplot of Cumulative Net Amount ($) by Description",
       x = "Description of Fund",
       y = "Cumulative Net Amount ($)")

agg_fund_plot
```


### b. Funct/Function
```{r}


temp_sequence_funct <- seq(from = 0, to = 5,  by = 1)

funct_plots<- temp_sequence_funct %>%
  map(
    barplot_description_amount,
    templist = osa_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_funct",
    uca_block = funct,
    uca_block_description = funct_description
  )

names(funct_plots) <- c("not_applicable",
                          "general_government",
                          "public_safety",
                          "public_works",
                          "health",
                          "community")

funct_plots # run funct_plots in console and view them easier than the markdown.
```


### c. Account

#### i.  Revenue
```{r}

#make plots by revenues ========================================================
temp_sequence_revenues <- seq(from = 3000, to = 3009,  by = 1)

revenue_plots<- temp_sequence_revenues %>%
  map(
    barplot_description_amount,
    templist = osa_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_account",
    uca_block = account,
    uca_block_description = account_description
  )

names(revenue_plots) <- c("revenues",
                  "taxes",
                  "licenses_and_permits",
                  "intergovernmental",
                  "charges_for_service",
                  "fines_and_forfeitures",
                  "miscellaneous",
                  "other_sources_of_funding",
                  "special_and_extraordinary_gain",
                  "suspense")
```

#### ii. Expenditures
```{r}
#Make plots for expenditures ===================================================
temp_sequence_expenditures <- seq(from = 4000, to = 4017,  by=1)

expenditure_plots<- temp_sequence_expenditures %>%
  map(
    barplot_description_amount,
    templist = osa_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_account",
    uca_block = account,
    uca_block_description = account_description
  )
names(expenditure_plots) <- c("expenditures",
                  "personnel_services",
                  "general_and_contracted_services",
                  "utilities_and_utility_services",
                  "taxes_and_fees",
                  "supplies_and_materials",
                  "grants_and_contracts",
                  "direct_payments",
                  "capital_outlays",
                  "interdepartmental_charges",
                  "judgements_and_losses",
                  "other_financing_uses",
                  "depreciation",
                  "amortiaton",
                  "bad_debt_expense",
                  "contingencies",
                  "special_and_extraordinary_loss",
                  "debt_service")

#consolidate objects
account_plots <- list(revenue_plots, expenditure_plots)
names(account_plots) <- c("revenue_plots", "expenditure_plots")

#remove redundant objects
rm(temp_sequence_revenues, temp_sequence_expenditures, revenue_plots, expenditure_plots)
```
####  iii. View
```{r}
#to see all plot simply run:
account_plots
```

To only view the revenue plots, we pluck it from the list.
```{r}
account_plots %>% pluck("revenue_plots") 
```

If you are only interested in a single plot, you need to pluck twice. shown below:
```{r}
temp <- account_plots %>% 
  pluck("expenditure_plots") %>% 
  pluck("capital_outlays")
temp
```

To access elements of the plot, use this code format. The code below selects the data frame used to generate the plot from intergovernmental revenue
```{r}
account_plots %>% 
  pluck("revenue_plots") %>%
  pluck("intergovernmental") %>%
  pluck("data")
```

##2. USBE

### a. Fund
```{r}
agg_fund_plot <-  usbe_agg_tables %>%
  pluck("agg_by_description_and_code") %>%
  pluck("agg_fund") %>% 
  ggplot(aes(x = fund_description, y = total_amount)) + geom_bar(stat = "identity", fill = "orchid2") +
  coord_flip() +
  geom_text(
    aes(label = paste0("$", total_amount)),
    hjust = "inward",
    vjust = 0,
    size = 2.5
  ) +
  labs(title = "Barplot of Cumulative Net Amount ($) by Description",
       x = "Description of Fund",
       y = "Cumulative Net Amount ($)")

agg_fund_plot
```
### b. Location

### c. Program
```{r}


temp_sequence <- seq(from = 0, to = 9,  by = 1)
#there is nothing in range 4000
temp_sequence <- temp_sequence[-5]


program_plots<- temp_sequence %>%
  map(
    barplot_description_amount,
    templist = usbe_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_program",
    uca_block = program,
    uca_block_description = program_description
  )

# names(funct_plots) <- c("not_applicable",
#                           "general_government",
#                           "public_safety",
#                           "public_works",
#                           "health",
#                           "community")

program_plots # run funct_plots in console and view them easier than the markdown.
```

### d. Funct/Function
```{r}


temp_sequence_funct <- seq(from = 1, to = 5,  by = 1)

funct_plots<- temp_sequence_funct %>%
  map(
    barplot_description_amount,
    templist = usbe_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_funct",
    uca_block = funct,
    uca_block_description = funct_description
  )

# names(funct_plots) <- c("not_applicable",
#                           "general_government",
#                           "public_safety",
#                           "public_works",
#                           "health",
#                           "community")

funct_plots # run funct_plots in console and view them easier than the markdown.
```

### e. object
```{r}
temp_sequence <- seq(from = 1, to = 8,  by = 1)

object_plots<- temp_sequence %>%
  map(
    barplot_description_amount,
    templist = usbe_agg_tables,
    agg_by_type= "agg_by_description_and_code",
    agg_type = "agg_object",
    uca_block = object,
    uca_block_description = object_description
  )


object_plots 
```
```{r}
object_plots %>% pluck(1) %>% pluck("data")
```

### f. revenue
right now everyone just puts in the 0000
```{r}
# temp_sequence <- seq(from = 0, to = 5,  by = 1)
# 
# revenue_plots <- temp_sequence %>%
#   map(
#     barplot_description_amount,
#     templist = usbe_agg_tables,
#     agg_by_type= "agg_by_description_and_code",
#     agg_type = "agg_revenue",
#     uca_block = revenue,
#     uca_block_description = revenue_description
#   )
# 
# 
# revenue_plots
```
#VII. Generate Invalid Report

## na_or_empty : Examine transactions with na or empty value for their account number
```{r}
invalid_tables %>% pluck("na_or_empty")
```

## invalid_length : Examine transactions with an account number too long or too small to fit either LEA or non-LEA UCOA.
```{r}
invalid_tables %>% pluck("invalid_length")
```

## invalid_lea_format : Examine transactions for LEAs with an account number with correct length, but incorrect format
```{r}
invalid_tables %>% pluck("invalid_lea_format")
```


## invalid_osa_format : Examine transactions for non LEAs with an account number with correct length, but incorrect format
```{r}
invalid_tables %>% pluck("invalid_osa_format")
```

## Unmapped codes
  * Note that for all, you can view more information. The data in each table is as follows:
    **id
    **batch_id
    **amount 
    **fiscal_year
    **account_number
    **type
    **fund
    **funct
    **...
    **fund_description
    **funct_description
    **...
### unmapped_fund_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the fund code provided does not map to the ucoa code spreadsheet
```{r}
invalid_tables %>% pluck("osa_unmapped_fund_code") %>% select(id, batch_id, amount, fund, fund_description)
```


### unmapped_fund_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the function code provided does not map to the ucoa code spreadsheet
```{r}
invalid_tables %>% pluck("osa_unmapped_funct_code") %>% select(id, batch_id, amount, funct,funct_code_primary, funct_code_secondary,funct_code_tertiary, funct_description, funct_level_primary, funct_level_secondary, funct_level_tertiary, )
```
### unmapped_account_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet
```{r}
invalid_tables %>% pluck("osa_unmapped_account_code") %>% select(id, batch_id, amount, account, account_description)
```

### lea_unmapped_fund_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_fund") %>% select(id, batch_id, amount, fund, fund_description)
```

### lea_unmapped_location_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_location") %>% select(id, batch_id, amount, location, location_description)
```

### lea_unmapped_program_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_program") %>% select(id, batch_id, amount, program, program_description)
```

### lea_unmapped_funct_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_funct") %>% select(id, batch_id, amount, funct, funct_description)
```

### lea_unmapped_object_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_object") %>% select(id, batch_id, amount, object, object_description)
```

### lea_unmapped_revenue_classification_code : Examine transactions for non LEAs with an account number with correct length, and correct format, but the account code provided does not map to the ucoa code spreadsheet

```{r}
invalid_tables %>% pluck("usbe_unmapped_revenue") %>% select(id, batch_id, amount, revenue, revenue_description)
```



```{r}
invalid_tables %>% pluck("usbe_fund_header") %>% select(id, batch_id, amount, fund, fund_description)
```
```{r}
invalid_tables %>% pluck("usbe_location_header") %>% select(id, batch_id, amount, location, location_description)
```

```{r}
invalid_tables %>% pluck("usbe_program_header") %>% select(id, batch_id, amount, program, program_description)
```


```{r}
invalid_tables %>% pluck("usbe_funct_header") %>% select(id, batch_id, amount, funct, funct_description)
```

```{r}
invalid_tables %>% pluck("usbe_object_header") %>% select(id, batch_id, amount, object, object_description)
```


```{r}
invalid_tables %>% pluck("usbe_revenue_header") %>% select(id, batch_id, amount, revenue, revenue_description)
```

