---
title: "osbe-batch-validation"
author: "Alexander Nielson"
date: "2/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Program Description

**Purpose**


**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "salesforce"
```

**Output(s)**

# Get Input
```{r}
validation_type <- 
#  "file_analysis"
 "batch_analysis"

if(validation_type=="batch_analysis") {
  entity_id <- 1010
}

if (validation_type == "file_analysis"){
  downloaded_file <- "location_of_pipe_delim_file.txt"
}
  

```


# Libraries and Data Sources

```{r}
options(scipen=999)

library(lubridate)
library(magrittr)
library(odbc)
library(readxl) 
library(tidyverse)
library(stringi) 
library(tidyr)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)

rm(dsn_aws, dsn_salesforce)

```

# Function Definitions

# Load Lookup Table

```{r}
usbe_lookup_file_name <- "usbe_lookup.xlsx"


usbe_lookup <- excel_sheets(usbe_lookup_file_name) %>%
  map(read_excel, path = usbe_lookup_file_name)

names(usbe_lookup) <- c("fund", "location", "program", "funct","object","revenue")

rm(usbe_lookup_file_name)

# manually add codes

# FUNCT - 0000
usbe_lookup$funct <- usbe_lookup %>% pluck("funct") %>% 
  bind_rows(tibble(number = "0000",
                   description = "TEMP-HOLDER-AN",
                   can_submit = TRUE))

# OBJECT - 000
usbe_lookup$object <- usbe_lookup %>% pluck("object") %>% 
  bind_rows(tibble(number = "000",
                   description = "TEMP-HOLDER-AN",
                   can_submit = TRUE))

# usbe_fund <- read_xlsx(usbe_lookup_file_name,
#           sheet = excel_sheets(usbe_lookup_file_name) %>% pluck(1) %>% pluck("fund"),
#           col_names = TRUE
#           )
#           
# 
# usbe_location <- read_xlsx(usbe_lookup_file_name,
#           sheet = excel_sheets(usbe_lookup_file_name)%>% pluck(1) %>% pluck("location"),
#           col_names = TRUE
#           ) %>% 
#   mutate(number = number %>% str_pad(3, pad = "0")) 
# 
# usbe_program <- read_xlsx(usbe_lookup_file_name,
#           sheet = excel_sheets(usbe_lookup_file_name) %>% pluck("program"),
#           col_names = TRUE
#           ) %>% 
#   mutate(number = number %>% str_pad(4, pad = "0")) 
# 
# 
# usbe_funct <- read_xlsx(usbe_lookup_file_name,
#           sheet = excel_sheets(usbe_lookup_file_name) %>% pluck("funct"),
#           col_names = TRUE
#           ) %>% 
#   mutate(number = number %>% str_pad(4, pad = "0")) 
# 
# usbe_object <- read_xlsx(usbe_lookup_file_name,
#           sheet = excel_sheets(usbe_lookup_file_name) %>% pluck("object"),
#           col_names = TRUE
#           ) %>% 
#   mutate(number = number %>% str_pad(3, pad = "0")) 
# 
# usbe_revenue <- read_xlsx(usbe_lookup_file_name,
#           sheet = excel_sheets(usbe_lookup_file_name) %>% pluck("revenue"),
#           col_names = TRUE
#           ) %>% 
#   mutate(number = number %>% str_pad(4, pad = "0")) 
# 
# usbe_lookup <- list(
#   fund     = usbe_fund,
#   location = usbe_location,
#   program  = usbe_program,
#   funct    = usbe_funct,
#   object   = usbe_object,
#   revenue  = usbe_revenue
# )

```

Remove unneeded objects
```{r}
# rm(
#   usbe_fund,
#   usbe_location,
#   usbe_funct,
#   usbe_program,
#   usbe_revenue,
#   usbe_object,
#   usbe_lookup_file_name
# )
```

```{r}
# temp <-
#   dbGetQuery(
#     odbc_aws,
#     paste(
#       "
#         SELECT *
#         FROM transaction t
#         JOIN entity e
#           ON e.id = t.entity_trans_id
#         WHERE t.fiscal_year = 2019
#         AND t.account_number IS NOT NULL
#         LIMIT 1000"
#     ))
  
```


```{r}
# 1. Query the database, get all the records that are not obviously missing data. 
transaction_report <-
  dbGetQuery(
    odbc_aws,
    paste(
      "
        SELECT id,
        batch_id,
        amount,
        fiscal_year,
        account_number,
        type
        FROM transaction
        WHERE fiscal_year = 2019
        AND account_number IS NOT NULL
        AND LENGTH(account_number) = 25
        LIMIT 1000000"
    )
  ) %>% 
  as_tibble()

# 2. double check for NA or "" -------------------------------------------------

invalid_reported_na <- transaction_report %>%
  filter(account_number == "",
         is.na(account_number))

transaction_report <-
  transaction_report %>%
  filter(account_number != "", !is.na(account_number))

# 3. check correct length ------------------------------------------------------

# 19 is for normal, 25 is for USBE (dashes are included in string legth)
invalid_length <- transaction_report %>%
  filter( nchar(account_number) != 25) %>%
  mutate(
    account_number_length = nchar(account_number),
    reason = case_when(
      account_number_length < 25 ~ paste("uca code block too short - length =", account_number_length),
      account_number_length > 25 ~ paste("uca code block too long - length =", account_number_length)
    )
  )

transaction_report <- transaction_report %>%
  filter(nchar(account_number) == 25)

# USBE validation ==============================================================

# check for valid form. ie: ##-###-####-####-###-#### 
 
invalid_form <-
  transaction_report %>%
  filter(!str_detect(
    .$account_number,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))

transaction_report <-
  transaction_report %>%
  filter(str_detect(
    .$account_number,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))


# consolidate ==================================================================
invalid_tables <- list(invalid_reported_na,
                       invalid_length,
                       invalid_form)



# remove unneeded objects ======================================================
# comment any object that you want to inspect in the global environment pane
rm(invalid_reported_na,
   invalid_length,
   invalid_form)
```

```{r}
transaction_save <- transaction_report
```

```{r}
transaction_report <- transaction_save
```

```{r}

transaction_report <- transaction_report %>%
  mutate(
    fund                   = .[["account_number"]] %>% substr(0, 2),
    location               = .[["account_number"]] %>% substr(4, 6),
    program                = .[["account_number"]] %>% substr(8, 11),
    funct                  = .[["account_number"]] %>% substr(13, 16),
    object                 = .[["account_number"]] %>% substr(18, 20),
    revenue                = .[["account_number"]] %>% substr(22, 25),
  ) %>%
  
# join the funds
left_join(
  usbe_lookup %>%
    pluck("fund") %>%
    select(
      number,
      fund_description = description,
      fund_can_submit = can_submit
    ),
  by = c("fund" = "number")
) %>%
  # join the functions
  left_join(
    usbe_lookup %>%
      pluck("location") %>%
      select(
        number,
        location_description = description,
        location_can_submit = can_submit
      ),
    by = c("location" = "number")
  ) %>%
  # join the accounts
  left_join(
    usbe_lookup %>%
      pluck("program") %>%
      select(
        number,
        program_description = description,
        program_can_submit = can_submit
      ),
    by = c("program" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("funct") %>%
      select(
        number,
        funct_description = description,
        funct_can_submit = can_submit
      ),
    by = c("funct" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("object") %>%
      select(
        number,
        object_description = description,
        object_can_submit = can_submit
      ),
    by = c("object" = "number")
  ) %>%
  left_join(
    usbe_lookup %>%
      pluck("revenue") %>%
      select(
        number,
        revenue_description = description,
        revenue_can_submit = can_submit
      ),
    by = c("revenue" = "number")
  )
```

```{r}
usbe_lookup$program %>% group_by(number) %>% summarize(n = n()) %>% filter(n>1)
usbe_lookup$object %>% group_by(number) %>% summarize(n = n()) %>% filter(n>1)
usbe_lookup$fund %>% group_by(number) %>% summarize(n = n()) %>% filter(n>1)
usbe_lookup$funct %>% group_by(number) %>% summarize(n = n()) %>% filter(n>1)
usbe_lookup$location %>% group_by(number) %>% summarize(n = n()) %>% filter(n>1)
usbe_lookup$revenue %>% group_by(number) %>% summarize(n = n()) %>% filter(n>1)
```


# Find unmapped UCA
*There are many reasons why this might be the case 
**They are using an old UCOA
**They pressed the incorrect key / typos
...regardless, they must be filtered out. 

```{r}
#find wrong fund code
bad_fund_code <- transaction_report %>%
  filter(!fund %in% (usbe_lookup %>%
                       pluck("fund")  %>%
                       select(number) %>%
                       unlist()))

#find wrong location code
bad_location_code<-transaction_report %>%
  filter(!location %in% (usbe_lookup %>%
                        pluck("location") %>%
                        select(number) %>%
                        unlist()))
#find wrong program code
bad_program_code <- transaction_report %>%
  filter(!program %in% (usbe_lookup %>%
                          pluck("program") %>%
                          select(number)   %>%
                          unlist()))

bad_funct_code <- transaction_report %>%
  filter(!funct %in% (usbe_lookup %>%
                          pluck("funct") %>%
                          select(number)   %>%
                          unlist()))

bad_object_code <- transaction_report %>%
  filter(!object %in% (usbe_lookup %>%
                          pluck("object") %>%
                          select(number)   %>%
                          unlist()))

bad_revenue_code <- transaction_report %>%
  filter(!revenue %in% (usbe_lookup %>%
                          pluck("revenue") %>%
                          select(number)   %>%
                          unlist()))

#Remove invalid codes.
transaction_report<- transaction_report %>%
  anti_join(bad_fund_code, by = "id") %>%
  anti_join(bad_location_code, by = "id") %>%
  anti_join(bad_program_code, by = "id") %>%
  anti_join(bad_funct_code, by = "id") %>%
  anti_join(bad_object_code, by = "id") %>%
  anti_join(bad_revenue_code, by = "id")

#consolidate ## FIX THE NAMEING FOR THE LIST.
invalid_tables <- c(invalid_tables,
    unmapped_fund = bad_fund_code,
    unmapped_location= bad_location_code,
    unmapped_program= bad_program_code,
    unmapped_funct= bad_funct_code,
    unmapped_object= bad_object_code,
    unmapped_revenue= bad_revenue_code
  )

```

Remove uneeded objects
```{r}
rm(
    bad_fund_code,
    bad_location_code,
    bad_program_code,
    bad_funct_code,
    bad_object_code,
    bad_revenue_code
  )
```



# Check for invalid header use 
entites which report using the USBE uca cannot use the header code number. the usbe gave me a document with a field called can_submit which essentially was a boolean for whether a code was or was not a header code. 
```{r}

fund_header <- transaction_report %>% 
  filter(fund_can_submit != TRUE)

location_header <- transaction_report %>% 
  filter(location_can_submit != TRUE)

program_header <- transaction_report %>% 
  filter(program_can_submit != TRUE)

funct_header <- transaction_report %>% 
  filter(funct_can_submit != TRUE)

object_header <- transaction_report %>% 
  filter(object_can_submit != TRUE)

revenue_header <- transaction_report %>% 
  filter(revenue_can_submit != TRUE)

transaction_report <- transaction_report %>% 
  anti_join(fund_header, by =c("id" = "id")) %>% 
  anti_join(location_header, by =c("id" = "id")) %>% 
  anti_join(program_header, by =c("id" = "id")) %>% 
  anti_join(funct_header, by =c("id" = "id")) %>% 
  anti_join(object_header, by =c("id" = "id")) %>% 
  anti_join(revenue_header, by =c("id" = "id"))  
  
# consolidate
invalid_header <- list(
  usbe_fund_header = fund_header,
  usbe_location_header = location_header,
  usbe_program_header = program_header,
  usbe_funct_header = funct_header,
  usbe_object_header = object_header,
  usbe_revenue_header = revenue_header
)
  
```

consolidate the invalid header usage into the invalid tables object
```{r}


invalid_tables <- c(invalid_tables,invalid_header)
```

Remove objects
```{r}
rm(
  invalid_header,
  fund_header,
  location_header,
  program_header,
  funct_header,
  object_header,
  revenue_header
)
```

```{r}
names(invalid_tables) <- c(
  "invalid_reported_na",
  "invalid_length",
  "invalid_form",
  "bad_fund_code",
  "bad_location_code",
  "bad_program_code",
  "bad_funct_code",
  "bad_object_code",
  "bad_revenue_code",
  "bad_fund_header",
  "bad_location_header",
  "bad_program_header",
  "bad_funct_header",
  "bad_object_header",
  "bad_revenue_header"
)
```

Since all uca now is mapped and valid I am going to get rid of unncessary columns
```{r}
transaction_report <- transaction_report %>%
  select(
    id,
    batch_id,
    amount,
    fiscal_year,
    account_number,
    type,
    fund,
    location,
    program,
    funct,
    object,
    revenue,
    fund_description,
    location_description,
    program_description,
    funct_description,
    object_description,
    revenue_description
  )
```

