---
title: "Vague UCoA Report"
author: "Michael Jensen"
date: "September 2019"
output: html_notebook
---
# Program Description

**Purpose**

For non-archived Transparent Utah data, determine the percentage of UCoA function and account codes that are vague. 

Valid-but-vague UCoA values are an obstacle to making the data useful for analysis. We want to identify entities with a high percentage of vague UCoA values so we can work with them to get more detailed financial information.

**Input(s)**

```{r}
dsn_aws        <- "transpAWS"
dsn_salesforce <- "salesforce"
```

**Output(s)**

* A .csv file containing the following for each active and participating entity with a Transparency ID listed in Salesforce:
  + The percentage of transactions that have a vague function code
  + The percentage of transactions that have a vague expense account code
  + The percentage of transactions that have a vague revenue account code

# Libraries and Data Sources

```{r}
library(lubridate)
library(magrittr)
library(odbc)
library(readxl)
library(tidyverse)

odbc_aws <- dbConnect(odbc::odbc(), dsn_aws)
odbc_sf  <- dbConnect(odbc::odbc(), dsn_salesforce)

rm(dsn_aws, dsn_salesforce)

download.file(
  "http://financialreports.utah.gov/chartofaccounts/ChartofAccountFull.xlsx",
  "ucoa.xlsx",
  mode = "wb")
```

# Function Definitions

## Argument Definitions

```{r, eval=FALSE}
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   ucoa (list): The list containing the Fund, Function, and Account codes 
  #     from OSA's Uniform Chart of Accounts.
  #   ucoa_type (char): The UCoA component to check ("funct" = function,
  #     "exp" = expense, "rev" = revenue).
```

## check_percentage_of_vague_ucoa

```{r}
check_percentage_of_vague_ucoa <- function(t_id, ucoa_type, ucoa) {
  # Determine the percentage of an entity's transactions that use a valid but 
  # vague UCoA code.
  #
  # Arguments:
  #   t_id (num): The entity's Transparency ID, as queried from Salesforce
  #     rather than Transparency.
  #   ucoa_type (char): The UCoA component to check ("funct" = function,
  #     "exp" = expense, "rev" = revenue).
  #   ucoa (list): The list containing the Fund, Function, and Account codes 
  #     from OSA's Uniform Chart of Accounts.
  #
  # Value:
  #   Numeric.
  # 
  # Comments:
  #   The UCoA code is the key to analyzing, in aggregate, local government 
  #   financial data. The UCoA code is minimally useful if governments are 
  #   using only the most general code (e.g., coding a transaction as
  #   100-000000-30000000 isn't useful).
  
  reported_ucoa <- 
    dbGetQuery(
      odbc_aws,
      paste("
            SELECT account_number, type
            FROM transaction
            WHERE batch_id IN (
              SELECT id
              FROM batch
              WHERE entity_id = ", t_id, "
              AND status IN ('PROCESSED', 'PROCESSING', 'DONTDELETE'))")) %>% 
    as_tibble() %>% 
    filter(nchar(account_number, allowNA = TRUE) == 19) %>% 
    filter(!is.na(account_number))

  if (ucoa_type == "funct") {
    
    vague_ucoa_codes <- ucoa[["vague_funct"]][["NUMBER"]]
    
    reported_ucoa <- 
      reported_ucoa %>% 
      .[["account_number"]] %>% 
      substr(5, 10)
    
  } else if (ucoa_type == "exp") {
    
    vague_ucoa_codes <- ucoa[["vague_exp"]][["NUMBER"]]
    
    reported_ucoa <- 
      reported_ucoa %>% 
      filter(type == 1) %>% 
      .[["account_number"]] %>% 
      substr(12, 19)
    
  } else if (ucoa_type == "rev") {
    
    vague_ucoa_codes <- ucoa[["vague_rev"]][["NUMBER"]]
    
    reported_ucoa <- 
      reported_ucoa %>% 
      filter(type == 2) %>% 
      .[["account_number"]] %>% 
      substr(12, 19)
  }
  
  reported_vague_ucoa <- 
    reported_ucoa[reported_ucoa %in% vague_ucoa_codes]
  
  percent_vague <- 
    (length(reported_vague_ucoa) / length(reported_ucoa)) * 100

  round(percent_vague)
}
```

# Execution

## Salesforce

```{r}
# Note that I do not query LEAs. They are managed by USBE, which uses a
# different chart of accounts. I also do not query higher education.

sf_data <-
  dbGetQuery(
    odbc_sf,
    paste("
          SELECT
            Account.Name                  AS name,
            Account.Id                    AS id,
            Account.Transparency_ID__c    AS t_id,
            Account.Fiscal_Year_Begins__c AS begin_fy,
            RecordType.DeveloperName      AS govt_type
          FROM Account
          JOIN RecordType
          ON Account.RecordTypeId = RecordType.Id
          WHERE Account.RecordTypeId IN (
            SELECT Id
            FROM RecordType
            WHERE DeveloperName IN (
            'AOG',
            'City',
            'Conservation_District',
            'County',
            'District_Health',
            'Housing',
            'Independent_Quasi_State_Entity',
            'Interlocal',
            'Local_and_Special_Service_District',
            'Mental_Health',
            'Redevelopment_Agency_Project_Area',
            'Town'))
          AND Account.Entity_Status__c IN (
            'Current',
            'On hold',
            'Delinquent',
            'Suspended')
          AND Account.Name NOT IN (
            'Intermountain Power Agency',
            'Utah Associated Municipal Power Systems',
            'Utah Municipal Power Agency')
          AND (
            Account.Expense_Revenue_Start_Date__c <= DATE() OR
            Account.Expense_Revenue_Start_Date__c IS NULL)")) %>%
  as_tibble()
```

## UCoA

```{r}
ucoa_fund <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[1]])

ucoa_function <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[2]])

ucoa_account <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[3]])

# Some of the code below will become unnecessary after I edit OSA's Uniform
# Chart of Accounts and publish it on the OSA website.

colnames(ucoa_fund)     <- ucoa_fund[2, ]
colnames(ucoa_function) <- c("NUMBER", ucoa_function[1, 2:4])
colnames(ucoa_account)  <- ucoa_account[2, ]

ucoa_fund     <- ucoa_fund     %>% slice(-1, -2)
ucoa_function <- ucoa_function %>% slice(-1)
ucoa_account  <- ucoa_account  %>% slice(-1, -2)

# I don't think I need the fund numbers in this code... hold on to it until I'm
# done with the program, just in case.
extra_fund_numbers <- 
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>% 
  as.character() %>% 
  enframe(name = NULL) %>% 
  rename("NUMBER" = "value") %>% 
  mutate("SHORT DESCRIPTION" = NA, "FULL DESCRIPTION" = NA, "DETAIL" = NA,
         NUMBER = if_else(nchar(NUMBER) == 2, 
                          str_pad(NUMBER, width = 3, side = "left", "0"), 
                          NUMBER))

ucoa_fund <- 
  ucoa_fund %>% 
  bind_rows(extra_fund_numbers)

ucoa_fund$NUMBER[[1]]     <- "010"
ucoa_fund$NUMBER[[2]]     <- "020"
ucoa_fund$NUMBER[[3]]     <- "030"
ucoa_function$NUMBER[[1]] <- "000000"

ucoa_account_exp <-
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^4"))

ucoa_account_rev <- 
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^3"))
  
# ucoa_account_w2 <- 
#   ucoa_account %>% 
#   filter(str_detect(NUMBER, "^4001"))

ucoa_vague_funct <- 
  ucoa_function %>% 
  filter(
    NUMBER == "000000" |
    NUMBER == "100000" |
    NUMBER == "200000" |
    NUMBER == "300000" |
    NUMBER == "400000" |
    NUMBER == "500000")

ucoa_vague_exp <- 
  ucoa_account_exp %>% 
  filter(
    NUMBER == "40000000" |
    NUMBER == "40010000" |
    NUMBER == "40020000" |
    NUMBER == "40030000" |
    NUMBER == "40040000" |
    NUMBER == "40050000" |
    NUMBER == "40060000" |
    NUMBER == "40070000" |
    NUMBER == "40080000" |
    NUMBER == "40110000" |
    NUMBER == "40170000" )

ucoa_vague_rev <- 
  ucoa_account_rev %>% 
  filter(
    NUMBER == "30000000" |
    NUMBER == "30010000" |
    NUMBER == "30020000" |
    NUMBER == "30030000" |
    NUMBER == "30040000" |
    NUMBER == "30050000" |
    NUMBER == "30060000" |
    NUMBER == "30070000" )

ucoa <-
  list(
    fund        = ucoa_fund,
    funct       = ucoa_function,
    account     = ucoa_account,
    account_exp = ucoa_account_exp,
    account_rev = ucoa_account_rev,
    vague_funct = ucoa_vague_funct,
    vague_exp   = ucoa_vague_exp,
    vague_rev   = ucoa_vague_rev)

rm(ucoa_fund, ucoa_function, ucoa_account, extra_fund_numbers, ucoa_account_exp,
   ucoa_account_rev, ucoa_vague_funct, ucoa_vague_exp, ucoa_vague_rev)
```

## Report

```{r}
# The error I occasionally see when I run the code below is:
# Error in nchar(account_number, keepNA = TRUE): invalid multibyte string,
# element 375181.
# I suspect the error may result from non-UTF-8 characters in the account_number
# string...
report <- 
  sf_data %>% 
  filter(!is.na(t_id)) %>% 
  mutate(
    percent_vague_function = 
      t_id %>%                 
      map_dbl(
        check_percentage_of_vague_ucoa, 
        "funct", 
        ucoa),
    percent_vague_exp = 
      t_id %>% 
      map_dbl(
        check_percentage_of_vague_ucoa,
        "exp",
        ucoa),
    percent_vague_rev = 
      t_id %>% 
      map_dbl(
        check_percentage_of_vague_ucoa,
        "rev",
        ucoa))
```

```{r}
report %>% 
  write_csv(
    paste0(getwd(), "/Vague UCoA Report.csv"))
```

# DBMS Disconnection

```{r}
dbDisconnect(odbc_aws, odbc_sf)
```