---
title: "ucoa_test_validation_lea"
author: "Alexander Nielson"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries 
```{r}
library(tidyverse)
library(readxl)
library(stringi)
```

# Load .txt file which needs UCA validation
```{r}
batch_file_path <- "E:\\rprojects\\Transparency-UCOA\\testing_batch_file_lea.txt"

batch_file <- read.csv(batch_file_path, header = FALSE, sep = "|")

# https://finance.utah.gov/wp-content/uploads/filelayout.pdf
names(batch_file) <- c("record_num",
                       "fiscal_yr",
                       "entity_name",
                       "f1", # fund level 1
                       "f2",
                       "f3",
                       "f4",
                       "o1", # organization_level_1_name
                       "o2",
                       "o3",
                       "o4",
                       "o5",
                       "o6",
                       "o7",
                       "o8",
                       "o9",
                       "o10",
                       "transaction_type",
                       "c1", # category level 1
                       "c2",
                       "c3",
                       "c4",
                       "c5",
                       "c6",
                       "c7",
                       "pcv_name", # payee/customer/vendor name
                       "payee_dba",
                       "vendor_id",
                       "posting_date",
                       "transaction_description",
                       "transaction_id",
                       "transaction_reference_id",
                       "contract_name",
                       "contract_number",
                       "position_title",
                       "hourly_rate",
                       "gender",
                       "amount",
                       "protection_indicator",
                       "uca_coding_block",
                        "p1", # program level 1 name
                       "p2",
                       "p3",
                       "p4",
                       "p5",
                       "p6",
                       "p7",
                       "funct1",
                       "funct2",
                       "funct3",
                       "funct4",
                       "funct5",
                       "funct6",
                       "funct7"
                       ) 

batch_file <- batch_file %>%
  select(record_num,
         fiscal_yr,
         transaction_id,
         amount,
         uca_coding_block) %>% 
  mutate(uca_coding_block = as.character(uca_coding_block))




```

# Generate UCOA lookup
```{r}
# Wrangle and fix the fund =====================================================
lea_ucoa_fund <-
  read_xlsx("lea_ucoa_2020.xlsx", sheet = excel_sheets("lea_ucoa_2020.xlsx")[[1]])

lea_ucoa_fund<- lea_ucoa_fund %>%
  replace(is.na(.), "") %>% 
  unite(NUMBER_DESCRIPTION, c(1:2), sep= " ") %>% 
  mutate(NUMBER_DESCRIPTION = trimws(NUMBER_DESCRIPTION) ) %>% 
  filter(NUMBER_DESCRIPTION != "") %>% 
  slice(6:n()) %>% 
  filter(str_detect(NUMBER_DESCRIPTION, regex("^[[:digit:]]{2}"))) %>%
   # get rid of rows which have a range ie: 27-29 and 61-69
  filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{2}-"))) %>% 
  filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{2} -"))) %>% 
  mutate(
    NUMBER = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\w+"),
    DESCRIPTION = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\s(.*)")
  )

##add back the ranges
extra_fund_numbers <- c(27:29, 61:69) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("NUMBER" = "value") %>%
  mutate(
    "DESCRIPTION" =
      case_when(
        NUMBER %in% (27:29) ~ "Special Revenue Funds - (Assigned by District)",
        NUMBER %in% (61:69) ~ "Interal Service Fund - (Assigned by District)"
      ),
    "NUMBER_DESCRIPTION" = paste(NUMBER, DESCRIPTION)
  )

lea_ucoa_fund <-
  lea_ucoa_fund %>%
  bind_rows(extra_fund_numbers)



# Wrangle "Location" ===========================================================
# lea_ucoa_Location <-
#   read_xlsx("lea_ucoa_2019.xlsx", sheet = excel_sheets("lea_ucoa_2019.xlsx")[[2]])
# 
# lea_ucoa_Location<- lea_ucoa_Location %>% select(NUMBER_DESCRIPTION = 1) %>% 
#   replace(is.na(.),"") %>% 
#   filter(NUMBER_DESCRIPTION != "") %>% 
#   slice(3:n())
#   
lea_ucoa_location<- c(0:499,600:999) %>%
  # str_pad(3, pad = "0") %>% 
  as.character() %>%
  enframe(name = NULL) %>%
  rename("NUMBER" = "value") %>%
    mutate( "DESCRIPTION" =
      case_when(
        as.numeric(NUMBER) <= 10    ~ "Pre School",
        as.numeric(NUMBER) >= 11 & as.numeric(NUMBER) <= 99   ~ "District Level",
        NUMBER %in% (100:299) ~ "Elementary Schools",
        NUMBER %in% (300:399) ~ "Middle Schools",
        NUMBER %in% (400:499) ~ "Junior High Schools/Middle Schools",
        NUMBER %in% (600:699) ~ "Special Schools, Secondary",
        NUMBER %in% (700:799) ~ "High Schools",
        NUMBER %in% (800:899) ~ "Special Schools, Elementary",
        NUMBER %in% (900:975) ~ "Private Schools",
        NUMBER %in% (976:999) ~ "Adult Education Schools"
      )) %>% 
  mutate(NUMBER = NUMBER %>% str_pad(3, pad = "0")) %>% 
  mutate("NUMBER_DESCRIPTION" = paste(NUMBER, DESCRIPTION))
  

# Wrangle "program" ============================================================

lea_ucoa_program <-
  read_xlsx("lea_ucoa_2020.xlsx", sheet = excel_sheets("lea_ucoa_2020.xlsx")[[3]])

lea_ucoa_program<- lea_ucoa_program %>% 
  replace(is.na(.), "") %>% 
  unite(NUMBER_DESCRIPTION, c(1:9), sep= " ") %>% 
  mutate(NUMBER_DESCRIPTION = trimws(NUMBER_DESCRIPTION) ) %>% 
  filter(NUMBER_DESCRIPTION != "") %>% 
  slice(6:n()) %>% 
  filter(str_detect(NUMBER_DESCRIPTION, regex("^[[:digit:]]{4}"))) %>%
   # get rid of rows which have a # but are a range ie: 27-29 and 61-69
  filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4}-"))) %>% 
  filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4} -"))) %>% 
  mutate(
    NUMBER = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\w+"),
    DESCRIPTION = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\s(.*)")
  )

extra_program_numbers<- c(2000:3699, # 2000 SCHOOL LEVEL PROGRAMS
                          5251:5290,  
                          7804:7809,
                          7811:7819,
                          7821:7829,
                          7831:7839,
                          7841:7849,
                          7851:7859,
                          7871:7879,
                          7891:7899,
                          7916:7919,
                          7911:7914,
                          7921:7929,
                          7931:7939,
                          7941:7949,
                          7951:7959) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("NUMBER" = "value") %>% 
    mutate( "DESCRIPTION" =
      case_when(
        NUMBER %in%(2000:2099) ~ "General School",
        NUMBER %in%(2100:2199) ~ "General Studentbody",
        NUMBER %in%(2200:3299) ~ "Instructional Classes",
        NUMBER %in%(3300:3599) ~ "Other Instructional Classes",
        NUMBER %in%(3600:3699) ~ "Student Activity Funds",
        
        NUMBER %in%(5251:5259) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        NUMBER %in%(5260:5269) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",
        NUMBER %in%(5270:5290) ~ "OTHER MINIMUM SCHOOL PROGRAMS - Reserved for Numbers Assigned by Districts",

        NUMBER %in%(7804:7809) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7811:7819) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7821:7829) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7831:7839) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7841:7849) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7851:7859) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7871:7879) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7891:7899) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7916:7919) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7911:7914) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7921:7929) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7931:7939) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7941:7949) ~ "(NCLB) Numbers reserved for districts",
        NUMBER %in%(7951:7959) ~ "(NCLB) Numbers reserved for districts"
        
      ),
      "NUMBER_DESCRIPTION" = paste(NUMBER, DESCRIPTION))

lea_ucoa_program <-
  lea_ucoa_program %>%
  bind_rows(extra_program_numbers)  

# Wrangle "Function" ===========================================================
lea_ucoa_function <-
  read_xlsx("lea_ucoa_2020.xlsx", sheet = excel_sheets("lea_ucoa_2020.xlsx")[[4]])

lea_ucoa_function<- lea_ucoa_function %>% 
  replace(is.na(.), "") %>% 
  unite(NUMBER_DESCRIPTION, c(1:9), sep= " ") %>% 
  mutate(NUMBER_DESCRIPTION = trimws(NUMBER_DESCRIPTION) ) %>% 
  filter(NUMBER_DESCRIPTION != "") %>% 
  slice(6:n()) %>% 
  filter(str_detect(NUMBER_DESCRIPTION, regex("^[[:digit:]]{4}"))) %>%
  # filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4}-"))) %>% 
  # filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4} -"))) %>% 
  mutate(
    NUMBER = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\w+"),
    DESCRIPTION = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\s(.*)")
  )

# Wrangle "Object" =============================================================

lea_ucoa_object <-
  read_xlsx("lea_ucoa_2020.xlsx", sheet = excel_sheets("lea_ucoa_2020.xlsx")[[5]])

lea_ucoa_object<- lea_ucoa_object %>% 
  replace(is.na(.), "") %>% 
  unite(NUMBER_DESCRIPTION, c(1:8), sep= " ") %>% 
  mutate(NUMBER_DESCRIPTION = trimws(NUMBER_DESCRIPTION) ) %>% 
  filter(NUMBER_DESCRIPTION != "") %>% 
  slice(6:n()) %>% 
  filter(str_detect(NUMBER_DESCRIPTION, regex("^[[:digit:]]{3}"))) %>%
  # filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4}-"))) %>% 
  # # filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4} -"))) %>% 
  mutate(
    NUMBER = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\w+"),
    DESCRIPTION = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\s(.*)")
  )

# Wrangle "Revenue Classification" =============================================
lea_ucoa_revenue_classification <-
  read_xlsx("lea_ucoa_2020.xlsx", sheet = excel_sheets("lea_ucoa_2020.xlsx")[[6]])

lea_ucoa_revenue_classification<- lea_ucoa_revenue_classification %>% replace(is.na(.), "") %>% 
  unite(NUMBER_DESCRIPTION, c(1:9), sep= " ") %>% 
  mutate(NUMBER_DESCRIPTION = trimws(NUMBER_DESCRIPTION) ) %>% 
  filter(NUMBER_DESCRIPTION != "") %>% 
  slice(6:n()) %>% 
  filter(str_detect(NUMBER_DESCRIPTION, regex("^[[:digit:]]{3}"))) %>%
  # filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4}-"))) %>% 
  # # filter(!str_detect(NUMBER_DESCRIPTION, regex("[[:digit:]]{4} -"))) %>% 
  mutate(
    NUMBER = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\w+"),
    DESCRIPTION = stri_extract_first(NUMBER_DESCRIPTION, regex = "\\s(.*)")
  )

  extra_revenue_numbers <- c("0000") %>%
    as.character() %>%
    enframe(name = NULL) %>%
    rename("NUMBER" = "value") %>%
    mutate(
      "DESCRIPTION" =
        case_when(
          NUMBER == "0000" ~ "TEMPORARY HOLDER - ALEX NIELSON",
        ),
      "NUMBER_DESCRIPTION" = paste(NUMBER, DESCRIPTION)
    )
  
  lea_ucoa_revenue_classification <-
    lea_ucoa_revenue_classification %>%
    bind_rows(extra_revenue_numbers)


#consolidate
lea_ucoa_lookup <- list(
  fund                   = lea_ucoa_fund,
  location               = lea_ucoa_location,
  program                = lea_ucoa_program,
  funct                  = lea_ucoa_function,
  object                 = lea_ucoa_object,
  revenue_classification = lea_ucoa_revenue_classification
)


rm(
  lea_ucoa_fund,
  lea_ucoa_location,
  lea_ucoa_function,
  lea_ucoa_program,
  lea_ucoa_revenue_classification,
  lea_ucoa_object,
  extra_program_numbers,
  extra_fund_numbers
)
```


#Execute

check for correct length
```{r}
invalid_length<-batch_file %>% 
  filter(nchar(uca_coding_block) != 25)

correct_ucoa <- batch_file %>% 
  anti_join(invalid_length, by = c("transaction_id"))


```


check if the osa code has correct format ie: ###-######-########
```{r}
# check if the codes are valid form. ie: ##-###-####-####-###-#### 
 
invalid_format <-
  correct_ucoa %>%
  filter(!str_detect(
    correct_ucoa$uca_coding_block,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))

correct_ucoa <-
  correct_ucoa %>%
  filter(str_detect(
    correct_ucoa$uca_coding_block,
    regex(
      "^[:digit:]{2}-[:alnum:]{3}-[:digit:]{4}-[:digit:]{4}-[:digit:]{3}-[:digit:]{4}$"
    )
  ))
```

##check that each uca fund, function, and account maps to the official uca

###Atomize the UCA field
```{r}
# This breaks out the account numbers into fund, function, and account. 
correct_ucoa <- correct_ucoa %>% 
  mutate(
    fund                   = .[["uca_coding_block"]] %>% substr(0, 2),
    location               = .[["uca_coding_block"]] %>% substr(4, 6),
    program                = .[["uca_coding_block"]] %>%  substr(8, 11),
    funct                  = .[["uca_coding_block"]] %>%  substr(13, 16),
    object                 = .[["uca_coding_block"]] %>%  substr(18, 20),
    revenue_classification = .[["uca_coding_block"]] %>%  substr(22, 25),
  ) %>% 

# temp_lea_ucoa<- lea_ucoa %>% 
#   mutate(
#     fund                   = .[["account_number"]] %>% substr(0, 2),
#     location               = .[["account_number"]] %>% substr(4, 6),
#     program                = .[["account_number"]] %>%  substr(8, 11),
#     funct                  = .[["account_number"]] %>%  substr(13, 16),
#     object                 = .[["account_number"]] %>%  substr(18, 20),
#     revenue_classification = .[["account_number"]] %>%  substr(22, 25),
#   ) %>% 
# Now we need to join ucoa.xlsx, so we know what the codes mean.

# join the funds
left_join(lea_ucoa_lookup %>%
            pluck("fund") %>%
            select(NUMBER, fund_description =`DESCRIPTION`),
          by = c("fund"="NUMBER")
          ) %>%
# join the functions
left_join(lea_ucoa_lookup %>%
            pluck("location") %>%
            select(NUMBER, location_description = `DESCRIPTION`),
          by = c("location" = "NUMBER")
          ) %>% 
# join the accounts
left_join(lea_ucoa_lookup %>% 
            pluck("program") %>% 
            select(NUMBER, program_description = `DESCRIPTION`),
          by = c("program" = "NUMBER")
          ) %>% 
left_join(lea_ucoa_lookup %>% 
            pluck("funct") %>%
          select(NUMBER, function_description = `DESCRIPTION`),
        by = c("funct" = "NUMBER")
        ) %>% 
left_join(lea_ucoa_lookup %>% 
            pluck("object") %>%
            select(NUMBER, object_description = `DESCRIPTION`),
          by = c("object" = "NUMBER")
          ) %>% 
left_join(lea_ucoa_lookup %>% 
            pluck("revenue_classification") %>%
            select(NUMBER, rev_class_description = `DESCRIPTION`),
          by = c("revenue_classification" = "NUMBER")
          )
```

#### Find a list of entities who used codes which do no map to the LEA UCA. 
*There are many reasons why this might be the case 
**They are using an old UCOA
**They pressed the incorrect key / typos
...regardless, they must be filtered out. 

```{r}
#find wrong fund code
lea_bad_fund_code <- correct_ucoa %>%
  filter(!fund %in% (lea_ucoa_lookup %>%
                       pluck("fund")  %>%
                       select(NUMBER) %>%
                       unlist()))

#find wrong location code
lea_bad_location_code<-correct_ucoa %>%
  filter(!location %in% (lea_ucoa_lookup %>%
                        pluck("location") %>%
                        select(NUMBER) %>%
                        unlist()))
#find wrong program code
lea_bad_program_code <- correct_ucoa %>%
  filter(!program %in% (lea_ucoa_lookup %>%
                          pluck("program") %>%
                          select(NUMBER)   %>%
                          unlist()))

lea_bad_funct_code <- correct_ucoa %>%
  filter(!funct %in% (lea_ucoa_lookup %>%
                          pluck("funct") %>%
                          select(NUMBER)   %>%
                          unlist()))

lea_bad_object_code <- correct_ucoa %>%
  filter(!object %in% (lea_ucoa_lookup %>%
                          pluck("object") %>%
                          select(NUMBER)   %>%
                          unlist()))

lea_bad_revenue_classification_code <- correct_ucoa %>%
  filter(!revenue_classification %in% (lea_ucoa_lookup %>%
                          pluck("revenue_classification") %>%
                          select(NUMBER)   %>%
                          unlist()))

#now remove incorrectly mapped. we will save them to report, but do not want them in our analysis.
# 
# lea_ucoa<- lea_ucoa %>%
#   anti_join(lea_bad_fund_code, by = "id") %>%
#   anti_join(lea_bad_location_code, by = "id") %>%
#   anti_join(lea_bad_program_code, by = "id") %>%
#   anti_join(lea_bad_funct_code, by = "id") %>%
#   anti_join(lea_bad_object_code, by = "id") %>%
#   anti_join(lea_bad_revenue_classification_code, by = "id")
#temp_lea_ucoa <- lea_ucoa

correct_ucoa<- correct_ucoa %>%
  anti_join(lea_bad_fund_code, by = "transaction_id") %>%
 # anti_join(lea_bad_location_code, by = "transaction_id") %>% # commented until I figure out how to better do the location codes.
  anti_join(lea_bad_program_code, by = "transaction_id") %>%
  anti_join(lea_bad_funct_code, by = "transaction_id") %>%
  anti_join(lea_bad_object_code, by = "transaction_id") %>%
  anti_join(lea_bad_revenue_classification_code, by = "transaction_id")

#consolidate



#remove objects

```

#Consolidate objects

```{r}
incorrect_ucoa <-
  list(
    invalid_length,
    invalid_format,
    lea_bad_fund_code,
    lea_bad_location_code,
    lea_bad_program_code,
    lea_bad_funct_code,
    lea_bad_object_code,
    lea_bad_revenue_classification_code
  )
names(incorrect_ucoa) <-
  c(
    "invalid_length",
    "invalid_format",
    "unmapped_fund_code",
    "unmapped_location_code",
    "unmapped_program_code",
    "unmapped_funct_code",
    "unmapped_object_code",
    "unmapped_revenue_classification_code"
  )
```

#remove unneeded objects
```{r}
rm(
  invalid_length,
  invalid_formatlea_bad_fund_code,
  lea_bad_location_code,
  lea_bad_program_code,
  lea_bad_funct_code,
  lea_bad_object_code,
  lea_bad_revenue_classification_code
)
```

#Markdown Reports
```{r}
incorrect_ucoa %>% pluck("invalid_length")
```
```{r}
incorrect_ucoa %>% pluck("invalid_format")
```

```{r}
incorrect_ucoa %>% pluck("unmapped_fund_code") %>% select(record_num, fiscal_yr, transaction_id, amount, fund, fund_description)
```

```{r}
incorrect_ucoa %>% pluck("unmapped_location_code") %>% select(record_num, fiscal_yr, transaction_id, amount, location, location_description)
```




```{r}
incorrect_ucoa %>% pluck("unmapped_funct_code") %>% select(record_num, fiscal_yr, transaction_id, amount, funct, function_description)
```

```{r}
incorrect_ucoa %>% pluck("unmapped_program_code") %>% select(record_num, fiscal_yr, transaction_id, amount, program, program_description)

```

```{r}
incorrect_ucoa %>% pluck("unmapped_object_code") %>% select(record_num, fiscal_yr, transaction_id, amount, object, object_description)

```

```{r}
incorrect_ucoa %>% pluck("unmapped_revenue_classification_code") %>% select(record_num, fiscal_yr, transaction_id, amount, revenue_classification, rev_class_description)
```


#Generate Report

*check with Tae or Jeremy to determine how they want a report formatted. *
```{r}

```

