---
title: "ucoa_test_validatation"
author: "Alexander Nielson"
date: "2/11/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries 
```{r}
library(tidyverse)
library(readxl)
```

# Load .txt file which needs UCA validation
```{r}
batch_file_path <- "E:\\rprojects\\Transparency-UCOA\\Cache County Drainage District 6_EX-RV_Upload_(Feb-06-2019--Dec-31-2019).txt"

batch_file <- read.csv(batch_file_path, header = FALSE, sep = "|")

# https://finance.utah.gov/wp-content/uploads/filelayout.pdf
names(batch_file) <- c("record_num",
                       "fiscal_yr",
                       "entity_name",
                       "f1", # fund level 1
                       "f2",
                       "f3",
                       "f4",
                       "o1", # organization_level_1_name
                       "o2",
                       "o3",
                       "o4",
                       "o5",
                       "o6",
                       "o7",
                       "o8",
                       "o9",
                       "o10",
                       "transaction_type",
                       "c1", # category level 1
                       "c2",
                       "c3",
                       "c4",
                       "c5",
                       "c6",
                       "c7",
                       "pcv_name", # payee/customer/vendor name
                       "payee_dba",
                       "vendor_id",
                       "posting_date",
                       "transaction_description",
                       "transaction_id",
                       "transaction_reference_id",
                       "contract_name",
                       "contract_number",
                       "position_title",
                       "hourly_rate",
                       "gender",
                       "amount",
                       "protection_indicator",
                       "uca_coding_block"#,
                       # "p1"#, # program level 1 name
                       # "p2",
                       # "p3",
                       # "p4",
                       # "p5",
                       # "p6",
                       # "p7",
                       # "funct1",
                       # "funct2",
                       # "funct3",
                       # "funct4",
                       # "funct5",
                       # "funct6",
                       # "funct7"
                       ) 

batch_file <- batch_file %>%
  select(record_num,
         fiscal_yr,
         transaction_id,
         amount,
         uca_coding_block) %>% 
  mutate(uca_coding_block = as.character(uca_coding_block))




```




# Generate UCOA lookup
```{r}
#note that excel_sheets() returns a list, hence the list access syntax.
#access in this way since it is a xlsx file.
ucoa_fund <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[1]] )

ucoa_function <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[2]] )

ucoa_account <- 
  read_xlsx("ucoa.xlsx", sheet = excel_sheets("ucoa.xlsx")[[3]] )

#Since the xlsx file was built to be readable, and not necessarily easily
#parsed, the first two rows must be cleaned. 

#fix the column names
colnames(ucoa_fund)     <- ucoa_fund[2, ]
colnames(ucoa_function) <- c("NUMBER", ucoa_function[1, 2:4])
colnames(ucoa_account)  <- ucoa_account[2, ]

#remove the useless rows.
ucoa_fund     <- ucoa_fund     %>% slice(-1, -2)
ucoa_function <- ucoa_function %>% slice(-1)
ucoa_account  <- ucoa_account  %>% slice(-1, -2)


extra_fund_numbers <-
  c(202:298, 302:398, 402:448, 452:498, 502:598, 602:698, 702:798) %>%
  as.character() %>%
  enframe(name = NULL) %>%
  rename("NUMBER" = "value") %>%
  mutate("SHORT DESCRIPTION" = NA,
         `FULL DESCRIPTION` = case_when(
            NUMBER %in% (202:298) ~ "Special Revenue Funds (as assigned by local government)",
            NUMBER %in% (302:398) ~ "Debt Service Funds (as assigned by local government)",
            NUMBER %in% (402:448) ~ "Capital Projects Funds (as assigned by local government)",
            NUMBER %in% (452:498) ~ "Permanent Funds (as assigned by local government)",
            NUMBER %in% (502:598) ~ "Enterprise Funds (as assigned by local government)",
            NUMBER %in% (602:698) ~ "Internal Service Funds (as assigned by local government)",
            NUMBER %in% (702:798) ~ "Trust and Agency Funds (as assigned by local government)"
                                        ),
         "DETAIL" = NA
    
         )

ucoa_fund <-
  ucoa_fund %>%
  bind_rows(extra_fund_numbers)

#fix some other random formattings. ie: 10 ==> 010

ucoa_fund$NUMBER[[1]]     <- "010"
ucoa_fund$NUMBER[[2]]     <- "020"
ucoa_fund$NUMBER[[3]]     <- "030"
ucoa_function$NUMBER[[1]] <- "000000"

#we want a table of just account expenditures
ucoa_account_exp <-
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^4"))# filter for any row which starts with 4,
                                  # this is because UCoA attributes anything in 
                                  # the 3000-3999 to revenues

#we also want a table of just account revenues. 
ucoa_account_rev <- 
  ucoa_account %>% 
  filter(str_detect(NUMBER, "^3"))# filter for any row which starts with 3
                                  # this is because UCoA attribtes anything in
                                  # the 3000-3999 to revenues

#if we want a table of just w2 information, then we should run this code too.  
# ucoa_account_w2 <- 
#   ucoa_account %>% 
#   filter(str_detect(NUMBER, "^4001"))


ucoa_vague_funct <- 
  ucoa_function %>% 
  filter(                #DESCRIPTION OF FUNCTION
    NUMBER == "000000" | # Not Applicable
    NUMBER == "100000" | # General Government
    NUMBER == "200000" | # Public Safety
    NUMBER == "300000" | # Public Works
    NUMBER == "400000" | # Health
    NUMBER == "500000")  # Community

ucoa_vague_exp <- 
  ucoa_account_exp %>% 
  filter(                  # DESCRIPTION of Expeditures accounts
    NUMBER == "40000000" | # Expenditures
    NUMBER == "40010000" | # Personnel Services
    NUMBER == "40020000" | # General and Contracted Services
    NUMBER == "40030000" | # Utilities and Utility Services
    NUMBER == "40040000" | # Taxes and Fees
    NUMBER == "40050000" | # Supplies and Materials
    NUMBER == "40060000" | # Grants and Contracts
    NUMBER == "40070000" | # Direct Payments
    NUMBER == "40080000" | # Capital Outlays
      # Notice that I think that 40090000 Interdepartmental Charges, and
      # 40100000 Judgements and Losses are considered non-vague. Since they
      # cannot be broken down further. If this ever change then we would need to
      # include them here.
    NUMBER == "40110000" | # Other financing Uses
      # As noted above, 40120000:40160000 cannot be broken down into more
      # specific accounts
    NUMBER == "40170000" ) # Debt Service

ucoa_vague_rev <- 
  ucoa_account_rev %>% 
  filter(                  # DESCRIPTION OF Revenue accounts
    NUMBER == "30000000" | # Revenues
    NUMBER == "30010000" | # Taxes
    NUMBER == "30020000" | # Licenses and Permits
    NUMBER == "30030000" | # Intergovernmental
    NUMBER == "30040000" | # Charges For Service
    NUMBER == "30050000" | # Fines and Forfeitures
    NUMBER == "30060000" | # Miscellaneous
    NUMBER == "30070000" ) # Other Sources of Funding

ucoa_lookup <-
  list(
    fund        = ucoa_fund,
    funct       = ucoa_function,
    account     = ucoa_account,
    account_exp = ucoa_account_exp,
    account_rev = ucoa_account_rev,
    vague_funct = ucoa_vague_funct,
    vague_exp   = ucoa_vague_exp,
    vague_rev   = ucoa_vague_rev)

rm(ucoa_fund, ucoa_function, ucoa_account, extra_fund_numbers, ucoa_account_exp,
   ucoa_account_rev, ucoa_vague_funct, ucoa_vague_exp, ucoa_vague_rev)
```


#Execute

check for correct length
```{r}
invalid_length<-batch_file %>% 
  filter(nchar(uca_coding_block) != 19)

correct_ucoa <- batch_file %>% 
  anti_join(invalid_length, by = c("transaction_id"))


```


check if the osa code has correct format ie: ###-######-########
```{r}
invalid_format <- correct_ucoa %>%
  filter(!str_detect(
    correct_ucoa$uca_coding_block,
    regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")
  ))

correct_ucoa <-
  correct_ucoa %>%
  filter(str_detect(
    correct_ucoa$uca_coding_block,
    regex("^[:digit:]{3}-[:digit:]{6}-[:digit:]{8}$")
  ))
```

##check that each uca fund, function, and account maps to the official uca

###Atomize the UCA field
```{r}
# This breaks out the account numbers into fund, function, and account. 


correct_ucoa <- correct_ucoa %>% 
  mutate(
    fund = .[["uca_coding_block"]] %>% substr(0, 3),
    funct = .[["uca_coding_block"]] %>% substr(5, 10),
    account = .[["uca_coding_block"]] %>%  substr(12, 19),
  ) %>% 

# Now we need to join ucoa.xlsx, so we know what the codes mean.

# join the funds
left_join(ucoa_lookup[["fund"]] %>%
            as_tibble() %>%
            select(NUMBER, fund_description =`FULL DESCRIPTION`),
          by = c("fund"="NUMBER")
          ) %>% 
# join the functions
left_join(ucoa_lookup[["funct"]] %>%
            as_tibble() %>%
            select(NUMBER, function_description = `FULL DESCRIPTION`),
          by = c("funct" = "NUMBER")
          ) %>% 
# join the accounts
left_join(ucoa_lookup[["account"]] %>% 
            as_tibble() %>% 
            select(NUMBER, account_description = `FULL DESCRIPTION`),
          by = c("account" = "NUMBER")
          )
```

###check the mappings
```{r}
#find wrong fund code
bad_fund_code <- correct_ucoa %>%
  filter(!fund %in% (ucoa_lookup %>%
                       pluck("fund")  %>%
                       select(NUMBER) %>%
                       unlist()))
#find wrong function code
bad_funct_code<-correct_ucoa %>%
  filter(!funct %in% (ucoa_lookup %>%
                        pluck("funct") %>%
                        select(NUMBER) %>%
                        unlist()))
#find wrong account code
bad_account_code <- correct_ucoa %>%
  filter(!account %in% (ucoa_lookup %>%
                          pluck("account") %>%
                          select(NUMBER)   %>%
                          unlist()))


#now remove incorrectly mapped. we will save them to report, but do not want them in our analysis.

correct_ucoa<- correct_ucoa %>% 
  anti_join(bad_fund_code, by = "transaction_id") %>% 
  anti_join(bad_funct_code, by = "transaction_id") %>% 
  anti_join(bad_account_code, by = "transaction_id")



#consolidate
# osa_non_mapping <- list(osa_bad_fund_code,osa_bad_funct_code,osa_bad_account_code)
# names(osa_non_mapping) <- c("unmapped_fund_code","unmapped_funct_code","unmapped_account_code")


#remove objects
# rm(osa_bad_fund_code,osa_bad_funct_code,osa_bad_account_code)
```

#Consolidate objects

```{r}

incorrect_ucoa <-
  list(invalid_length,
       invalid_format,
       bad_fund_code,
       bad_funct_code,
       bad_account_code)
names(incorrect_ucoa) <-
  c(
    "invalid_length",
    "invalid_format",
    "unmapped_fund_code",
    "unmapped_funct_code",
    "unmapped_account_code"
  )
```

#remove unneeded objects
```{r}
rm(invalid_length,
       invalid_format,
       bad_fund_code,
       bad_funct_code,
       bad_account_code)
```

#Markdown Reports
```{r}
incorrect_ucoa %>% pluck("invalid_length")
```
```{r}
incorrect_ucoa %>% pluck("invalid_format")
```

```{r}
incorrect_ucoa %>% pluck("unmapped_fund_code") %>% select(record_num, fiscal_yr, transaction_id, amount, fund, fund_description)
```

```{r}
incorrect_ucoa %>% pluck("unmapped_funct_code") %>% select(record_num, fiscal_yr, transaction_id, amount, funct, function_description)
```

```{r}
incorrect_ucoa %>% pluck("unmapped_account_code") %>% select(record_num, fiscal_yr, transaction_id, amount, account, account_description)
```


#Generate Report

*check with Tae or Jeremy to determine how they want a report formatted. *
```{r}

```

